---
title: "230920_Exp40E_spo13m2"
output:
  html_document: default
  pdf_document: default
---


# Setup
```{r setup, include=FALSE}

# set folder to save to
setwd("/Users/lkoch/Lori MS RStudio/230920_Exp40E")
getwd()

#Load libraries ######

#library(reshape2)
library(ggplot2)
library(pheatmap)
library(dplyr)
#library(seqinr)
#library(corrplot)
#library(Rtsne)
#library(gProfileR)
library(tidyr)
library(matrixStats)
library(forcats)
library(limma)
#library(ggVennDiagram)
library(ggrepel)
library(plotly)
library(ggseqlogo)
library(gprofiler2)
library(stringr)
library(gtools)
library(ggpubr)
library(clipr)
library(scales)
library(data.table)
library(glue)
library(openxlsx)
library(patchwork)

# Functions


# TL functions

colMedians <- function (df, na.rm = T) {
  apply(df, 2, median, na.rm)
}

strsplit.extract <- function (x, split, index) {
  x <- as.character(x)
  x[x == ""] <- ";"
  x <- sapply(strsplit(x, split, fixed = TRUE), "[[", index)
  return(x)
}

#choosing number of clusters for k-means

wssplot <- function(data, nc=20, seed=1234, iter.max = 10){
  wss <- (nrow(data)-1)*sum(apply(data,2,var))
  for (i in 2:nc){
    set.seed(seed)
    wss[i] <- sum(kmeans(data, centers=i, iter.max = iter.max)$withinss)}
  plot(1:nc, wss, type="b", xlab="Number of Clusters",
       ylab="Within groups sum of squares")}

# LK Plotting to PDF function

print_plot<-function(plot,filename.pdf,width,height){
    print(plot)
pdf(filename.pdf, width=width, height=height) 
print(plot)
dev.off()
}


```


# load data tables

```{r,echo=F,message=F,warning=F}
#Read data tables #####

phosphos <- read.delim("/Users/lkoch/Lori MS RStudio/2305_Exp40E_spo13-m2/Phospho (STY)Sites.txt")

protg <- read.delim("/Users/lkoch/Lori MS RStudio/2305_Exp40E_spo13-m2/proteinGroups.txt")

#evi <- read.delim("/Users/lkoch/Lori MS RStudio/2305_Exp40E_spo13-m2/evidence.txt")

```



# rename columns
```{r,echo=F,message=F,warning=F}

#Remove reverse & contaminant #####

phosphos <- subset(phosphos, Reverse != "+" & Potential.contaminant != "+")
protg <- subset(protg, Reverse != "+" & Potential.contaminant != "+")

colnames(protg)[colnames(protg) == "id"] <- "protg.id"
colnames(phosphos)[colnames(phosphos) == "id"] <- "phosphos.id"

# set col names

protg_reporter_cols<-grep("Reporter.intensity.corrected...40E_N",colnames(protg),value=T)

phosphos_reporter_cols<-grep("Reporter.intensity.corrected...40E_PE___1",colnames(phosphos),value=T)

# copy and rename cols
# key
# 1= 8067 (WT) Rep1 
# 2= 26213 (spo13) Rep1
# 3= 32114 (spo13-m2) Rep1
# 4= 8067 (WT) Rep2
# 5= 26213 (spo13) Rep2
# 6= 32114 (spo13-m2) Rep2
# 7= 8067 (WT) Rep3
# 8= 26213 (spo13) Rep3
# 9= 32114 (spo13-m2) Rep3
# 10= 8067 (WT) Rep4

raw_cols<-c(paste0(c("WT","spo13","spo13m2"),"_Rep1"),paste0(c("WT","spo13","spo13m2"),"_Rep2"),paste0(c("WT","spo13","spo13m2"),"_Rep3"),"WT_Rep4")

protg[,raw_cols]<-protg[,protg_reporter_cols]
phosphos[,raw_cols]<-phosphos[,phosphos_reporter_cols]

```

# Make gene name col
```{r,echo=F,message=F,warning=F}

### Make gene name cols ####

### #load yeast gene map table
#I downloaded this file from https://www.uniprot.org/docs/yeast
#I modified the original file so it only includes the table and not the heading part at the top

gene.map.table <-read.csv("/Users/lkoch/Lori MS RStudio/Reference dataframes/Yeast_Uniprot2.csv")

#data prep so there isn't white space and only the first gene name is in the gene column
gene.map.table$Gene<-trimws(gene.map.table$Gene, "right")
gene.map.table$Gene.name <- strsplit.extract(gene.map.table$Gene, ";",1)

#### Create new ID columns ####
#Create a Gene.name column in phosphos table

phosphos$Gene.name <- gene.map.table$Gene.name[match(phosphos$Protein, gene.map.table$OLN)]

#### Create new ID cols in the protg table ####
#Create new Majority.protein.ID col with only FIRST (one) majority protein ID
#for cross referencing prot between tables

protg$Majority.protein.ID <- strsplit.extract(protg$Majority.protein.IDs, ";",1)

#Create Gene.name col in the protg table
protg$Gene.name <- gene.map.table$Gene.name[match(protg$Majority.protein.ID,gene.map.table$OLN)]
```

## Raw int plots

```{r, echo=FALSE}

# Replace zeros with NAs in reporter.cols, save in raw_cols so stats can be calc and plots made
# reporter_cols retain zeros
# raw_cols have zeros replaced with NAs

protg.DT<-as.data.table(protg)
phosphos.DT<-as.data.table(phosphos)

protg.DT[,c(raw_cols) := lapply(.SD,function(x) ifelse(x==0,NA,x)), .SD=protg_reporter_cols]
phosphos.DT[,c(raw_cols) := lapply(.SD,function(x) ifelse(x==0,NA,x)), .SD=phosphos_reporter_cols]

protg<-as.data.frame(protg.DT)
phosphos<-as.data.frame(phosphos.DT)

# protg boxplot
# all proteins no Zeros/NAs across entire timecourse
# protg %>%
#     filter(if_all(raw_cols,is.finite)) %>%
#   pivot_longer(cols=all_of(raw_cols),names_to="sample",values_to="intensity") %>% select(sample,intensity) %>%
#   ggplot(aes(x=fct_inorder(sample),y=log2(intensity),fill=sample)) +
#   geom_boxplot(aes(fill=sample),position="dodge",outlier.size = 0.25, notch = TRUE, size = 0.25)+
#   theme_classic()+
#   labs(y="log2 intensity",x="sample")+
#   theme(axis.text.x = element_text(angle=90,vjust=0.6),legend.position="none")+
#   ggtitle(paste0("protg raw, n=",nrow(protg %>%
#     filter(if_all(raw_cols,is.finite)))))
# 
# # phosphos boxplot
# phosphos %>%
#     filter(if_all(raw_cols,is.finite)) %>%
#   pivot_longer(cols=all_of(raw_cols),names_to="sample",values_to="intensity") %>% select(sample,intensity) %>%
#   ggplot(aes(x=fct_inorder(sample),y=log2(intensity),fill=sample)) +
#   geom_boxplot(aes(fill=sample),position="dodge",outlier.size = 0.25, notch = TRUE, size = 0.25)+
#   theme_classic()+
#   labs(y="log2 intensity",x="sample")+
#   theme(axis.text.x = element_text(angle=90,vjust=0.6),legend.position="none")+
#   ggtitle(paste0("phosphos raw, n=",nrow(phosphos %>%
#     filter(if_all(raw_cols,is.finite)))))

# number of sitess with finite values across all 10 conditions and with high localization score
# phosphos %>%
#     filter(if_all(raw_cols,is.finite)) %>%
#     filter(Localization.prob>0.75) %>% nrow() #7326


# raw data
boxplot(log2(protg[,raw_cols]),main="raw protein",ylab="log2 intensity")
boxplot(log2(phosphos[,raw_cols]),main="raw phosphos",ylab="log2 intensity")


```

# ColMedian Normalization
```{r,echo=F,message=F,warning=F}

# Normalization of protg and phosphos to reporter medians ####

# calculate protg reporter MEDIAN intensities
tot_med <- colMedians(protg[,raw_cols],na.rm=T)

# create new column names for normalised intensities
norm.tmt.cols <- paste0("norm_",raw_cols)

## normalise protg intensities
## by dividing by median of each reporter

# # Identify the target median, which in this case is the median of the median of each experiment

target_median <- median(tot_med)

# # # Identify the scaling factors needed to scale each individual experiment to reach the target_med
scaling_factors <- as.numeric( target_median / tot_med )

# # Scale the TMT intensities of each experiment so the median becomes the target median

protg[,norm.tmt.cols] <- sweep(protg[,raw_cols], 2, scaling_factors, FUN = "*")

# # check the colMedians are now the same
#colMedians(protg[,norm.tmt.cols])

# Channel/Column norm for phosphos data: ###

# calculate protg reporter MEDIAN intensities
phos_tot_med <- colMedians(phosphos[,raw_cols],na.rm=T)

# # Identify the target median, which in this case is the median of the median of each experiment

phos_target_median <- median(phos_tot_med)

# # # Identify the scaling factors needed to scale each individual experiment to reach the target_med
phos_scaling_factors <- as.numeric( phos_target_median / phos_tot_med )

# # Scale the TMT intensities of each experiment so the median becomes the target median

phosphos[,norm.tmt.cols] <- sweep(phosphos[,raw_cols], 2, phos_scaling_factors, FUN = "*")

# # check the colMedians
#colMedians(phosphos[,norm.tmt.cols])

# Boxplots of colNorm data
boxplot(log2(protg[,norm.tmt.cols]),main="colNorm protein",ylab="log2 intensity")
boxplot(log2(phosphos[,norm.tmt.cols]),main="colNorm phosphos",ylab="log2 intensity")

```

# Phos/Prot Norm

```{r,echo=F,message=F,warning=F}

##### New values called "stoic" for "stoichiometric" 

# extract first sequence window (some phos-sites have multiple and
# this messes up motif analysis)
phosphos$Sequence.window <- strsplit.extract(phosphos$Sequence.window, ';', 1)

#create new phos.stoic.cols 
phos.stoic.cols <- gsub("norm","stoic", norm.tmt.cols)

# data prep
#copy protg IDs in phosphos df to new column called first.protg.id
#this is necessary for matching protg.ids between the phosphos and protg table

phosphos$first.protg.id <- strsplit.extract(phosphos$Protein.group.IDs, ';', 1)

phos.stoic.temp.df <- protg[match(phosphos$first.protg.id, protg$protg.id), norm.tmt.cols]

#this divides the intensity of the phosphos over the protg
#normalized intensity then multiplies by 1000 (to get easier number)
#This creates "stoichiometric" phos. site changes...

phosphos[,phos.stoic.cols] <- mapply(function(x,y) {x/y},phosphos[,norm.tmt.cols],  phos.stoic.temp.df[,norm.tmt.cols]) * 1000

# check colMedians - they are close but not the same
#colMedians(phosphos[,phos.stoic.cols])

# Plot the phos.stoic.colss (normalized to protg)
boxplot(log2(phosphos[,phos.stoic.cols]),main="Phos/protg norm phosphos",ylab="log2 intensity")

```

# add gene.name_site col
```{r, message=FALSE, warning=FALSE, echo=F}

phosphos<-phosphos %>%
  mutate(gene.name_site=paste(Gene.name,Amino.acid,Positions.within.proteins,sep="-"))

```

# Change NAs back to Zeros

```{r,echo=F,message=F,warning=F}

# head(phosphos[,phosphos_reporter_cols]) # mostly zeros raw
# head(phosphos[,phos.stoic.cols]) # all zeros are NAs

protg.DT<-as.data.table(protg)
phosphos.DT<-as.data.table(phosphos)

nona_norm.tmt.cols<-paste0("nona_",norm.tmt.cols)
nona_phos.stoic.cols<-paste0("nona_",phos.stoic.cols)

# norm cols
protg.DT[,c(nona_norm.tmt.cols) := lapply(.SD,function(x) ifelse(is.na(x),0,x)), .SD=norm.tmt.cols]
phosphos.DT[,c(nona_phos.stoic.cols) := lapply(.SD,function(x) ifelse(is.na(x),0,x)), .SD=phos.stoic.cols]

protg<-as.data.frame(protg.DT)
phosphos<-as.data.frame(phosphos.DT)

```


# fold change between medians
```{r,echo=F,message=F,warning=F}

# nona_norm.tmt.cols[c(1,4,7,10)] # WT
# nona_norm.tmt.cols[c(2,5,8)] # spo13
# nona_norm.tmt.cols[c(3,6,9)] # spo13-m2

protg <- protg %>%
    mutate(WT_spo13_fc=apply(.[,nona_norm.tmt.cols],1,function(x) {median(c(x[1],x[4],x[7],x[10]))/median(c(x[2],x[5],x[8]))})) %>%
    mutate(WT_spo13m2_fc=apply(.[,nona_norm.tmt.cols],1,function(x) {median(c(x[1],x[4],x[7],x[10]))/median(c(x[3],x[6],x[9]))})) %>%
    mutate(spo13_spo13m2_fc=apply(.[,nona_norm.tmt.cols],1,function(x) {median(c(x[2],x[5],x[8]))/median(c(x[3],x[6],x[9]))}))


phosphos <- phosphos %>%
    mutate(WT_spo13_fc=apply(.[,nona_phos.stoic.cols],1,function(x) {median(c(x[1],x[4],x[7],x[10]))/median(c(x[2],x[5],x[8]))})) %>%
    mutate(WT_spo13m2_fc=apply(.[,nona_phos.stoic.cols],1,function(x) {median(c(x[1],x[4],x[7],x[10]))/median(c(x[3],x[6],x[9]))})) %>%
    mutate(spo13_spo13m2_fc=apply(.[,nona_phos.stoic.cols],1,function(x) {median(c(x[2],x[5],x[8]))/median(c(x[3],x[6],x[9]))}))

```

# t.test between samples

```{r,echo=F,message=F,warning=F}

# alltimes<-c("0","45","60","75","90","105","120","135","150","165")
# 
# # # t.tests must be done in for-loop
# pvals<-paste0("pval.",alltimes[2:10])

# nona_norm.tmt.cols[c(1,4,7,10)] # WT
# nona_norm.tmt.cols[c(2,5,8)] # spo13
# nona_norm.tmt.cols[c(3,6,9)] # spo13-m2

# note 0 v 0 will give NaN p-value
# 
# protg comparisons
# 
# protg 3 reps
# protg_3reps[,"WT_spo13_pval"]<-as.data.frame(apply(protg_3reps[,nona_norm.tmt.cols], 1, function(x){
#     ifelse(all(is.finite(x))&sum(x>0)>=1,t.test(x[c(1,4,7,10)],x[c(2,5,8)])$p.value,NA)}))
# # if you don't include the sum(x>0)>=1 then you get some NaN pvalues from 0v0
# 
# protg_3reps[,"WT_spo13m2_pval"]<-as.data.frame(apply(protg_3reps[,nona_norm.tmt.cols], 1, function(x){
#     ifelse(all(is.finite(x))&sum(x>0)>=1,t.test(x[c(1,4,7,10)],x[c(3,6,9)])$p.value,NA)}))
# 
# protg_3reps[,"spo13_spo13m2_pval"]<-as.data.frame(apply(protg_3reps[,nona_norm.tmt.cols], 1, function(x){
#     ifelse(all(is.finite(x))&sum(x>0)>=1,t.test(x[c(2,5,8)],x[c(3,6,9)])$p.value,NA)}))

# all protg
protg[,"WT_spo13_pval"]<-as.data.frame(apply(protg[,nona_norm.tmt.cols], 1, function(x){
    ifelse(all(is.finite(x))&sum(x>0)>=1,t.test(x[c(1,4,7,10)],x[c(2,5,8)])$p.value,NA)}))
# if you don't include the sum(x>0)>=1 then you get some NaN pvalues from 0v0

protg[,"WT_spo13m2_pval"]<-as.data.frame(apply(protg[,nona_norm.tmt.cols], 1, function(x){
    ifelse(all(is.finite(x))&sum(x>0)>=1,t.test(x[c(1,4,7,10)],x[c(3,6,9)])$p.value,NA)}))

protg[,"spo13_spo13m2_pval"]<-as.data.frame(apply(protg[,nona_norm.tmt.cols], 1, function(x){
    ifelse(all(is.finite(x))&sum(x>0)>=1,t.test(x[c(2,5,8)],x[c(3,6,9)])$p.value,NA)}))

# phosphos 3 reps
# phosphos_3reps[,"WT_spo13_pval"]<-as.data.frame(apply(phosphos_3reps[,nona_phos.stoic.cols], 1, function(x){
#     ifelse(all(is.finite(x))&sum(x>0)>=2,t.test(x[c(1,4,7,10)],x[c(2,5,8)])$p.value,NA)})) # sum(x>0)>=1 returned 4 NaN pvalues but >=2 returned 0 #sum(is.nan(phosphos_3reps$WT_spo13_pval))
# 
# phosphos_3reps[,"WT_spo13m2_pval"]<-as.data.frame(apply(phosphos_3reps[,nona_phos.stoic.cols], 1, function(x){
#     ifelse(all(is.finite(x))&sum(x>0)>=2,t.test(x[c(1,4,7,10)],x[c(3,6,9)])$p.value,NA)})) 
# 
# phosphos_3reps[,"spo13_spo13m2_pval"]<-as.data.frame(apply(phosphos_3reps[,nona_phos.stoic.cols], 1, function(x){
#     ifelse(all(is.finite(x))&sum(x>0)>=2,t.test(x[c(2,5,8)],x[c(3,6,9)])$p.value,NA)})) 

# # phosphos 2 reps
# phosphos_2reps[,"WT_spo13_pval"]<-as.data.frame(apply(phosphos_2reps[,nona_phos.stoic.cols], 1, function(x){
#     ifelse(all(is.finite(x))&sum(x>0)>=2,t.test(x[c(1,4,7,10)],x[c(2,5,8)])$p.value,NA)})) # sum(x>0)>=1 returned 4 NaN pvalues but >=2 returned 0 #sum(is.nan(phosphos_2reps$WT_spo13_pval))
# 
# phosphos_2reps[,"WT_spo13m2_pval"]<-as.data.frame(apply(phosphos_2reps[,nona_phos.stoic.cols], 1, function(x){
#     ifelse(all(is.finite(x))&sum(x>0)>=2,t.test(x[c(1,4,7,10)],x[c(3,6,9)])$p.value,NA)})) 
# 
# phosphos_2reps[,"spo13_spo13m2_pval"]<-as.data.frame(apply(phosphos_2reps[,nona_phos.stoic.cols], 1, function(x){
#     ifelse(all(is.finite(x))&sum(x>0)>=2,t.test(x[c(2,5,8)],x[c(3,6,9)])$p.value,NA)})) 

# all phosphos
phosphos[,"WT_spo13_pval"]<-as.data.frame(apply(phosphos[,nona_phos.stoic.cols], 1, function(x){
    ifelse(all(is.finite(x))&sum(x>0)>=2,t.test(x[c(1,4,7,10)],x[c(2,5,8)])$p.value,NA)})) # sum(x>0)>=1 returned 4 NaN pvalues but >=2 returned 0 #sum(is.nan(phosphos$WT_spo13_pval))

phosphos[,"WT_spo13m2_pval"]<-as.data.frame(apply(phosphos[,nona_phos.stoic.cols], 1, function(x){
    ifelse(all(is.finite(x))&sum(x>0)>=2,t.test(x[c(1,4,7,10)],x[c(3,6,9)])$p.value,NA)})) 

phosphos[,"spo13_spo13m2_pval"]<-as.data.frame(apply(phosphos[,nona_phos.stoic.cols], 1, function(x){
    ifelse(all(is.finite(x))&sum(x>0)>=2,t.test(x[c(2,5,8)],x[c(3,6,9)])$p.value,NA)})) 

pvals<-grep("pval",colnames(protg),value=T)
fcs<-grep("fc",colnames(protg),value=T)


```

# Call significance

```{r,echo=F,message=F,warning=F}

# add col to indiciate whether comparison is significantly different based on fold change and pvalue

# there are NaN fold changes from 0/0 and Inf fold changes from 2/0 comparisons
# there are NA pvalues from t.test(c(0,0),c(0,0)) comparisons
# therefore there needs to be a way to indicate that the comparison between those conditions is not sig
# I added a layer to the ifelse to first test whether thee fc and pval are finite, which NaN and Inf, NA are not
# things with non-finite fold changes and/or pvalues are not considered sig.


# EDIT changing the comparison labels so mutant comes first
# WT v spo13 WT_INCR = spo13_DECR
# WT v spo13 WT_DECR = spo13_INCR
# WT v spo13m2 WT_INCR = spo13m2_DECR
# WT v spo13m2 WT_DECR = spo13m2_INCR
# LEAVE THIS AS IS
# spo13 v spo13m2 spo13_INCR
# spo13 v spo13m2 spo13_DECR

# protg
protg <- protg %>%
   mutate(spo13_WT_sig=ifelse(is.finite(WT_spo13_fc)&is.finite(WT_spo13_pval),
                              ifelse(WT_spo13_fc>1.5 & WT_spo13_pval < 0.05,"DECR",
                                  ifelse(WT_spo13_fc<(1/1.5) & WT_spo13_pval < 0.05,"INCR","NC")),"NC")) %>%
    mutate(spo13m2_WT_sig=ifelse(is.finite(WT_spo13m2_fc)&is.finite(WT_spo13m2_pval),
                              ifelse(WT_spo13m2_fc>1.5 & WT_spo13m2_pval < 0.05,"DECR",
                                  ifelse(WT_spo13m2_fc<(1/1.5) & WT_spo13m2_pval < 0.05,"INCR","NC")),"NC")) %>%
    mutate(spo13_spo13m2_sig=ifelse(is.finite(spo13_spo13m2_fc)&is.finite(spo13_spo13m2_pval),
                              ifelse(spo13_spo13m2_fc>1.5 & WT_spo13m2_pval < 0.05,"INCR",
                                  ifelse(WT_spo13m2_fc<(1/1.5) & WT_spo13m2_pval < 0.05,"DECR","NC")),"NC")) %>%
    # adjust so factor levels are all the same
     mutate(spo13_WT_sig=factor(spo13_WT_sig,levels=c("NC","INCR","DECR"))) %>%
     mutate(spo13m2_WT_sig=factor(spo13m2_WT_sig,levels=c("NC","INCR","DECR"))) %>%
     mutate(spo13_spo13m2_sig=factor(spo13_spo13m2_sig,levels=c("NC","INCR","DECR")))

# phosphos
phosphos <- phosphos %>%
   mutate(spo13_WT_sig=ifelse(is.finite(WT_spo13_fc)&is.finite(WT_spo13_pval),
                              ifelse(WT_spo13_fc>1.5 & WT_spo13_pval < 0.05,"DECR",
                                  ifelse(WT_spo13_fc<(1/1.5) & WT_spo13_pval < 0.05,"INCR","NC")),"NC")) %>%
    mutate(spo13m2_WT_sig=ifelse(is.finite(WT_spo13m2_fc)&is.finite(WT_spo13m2_pval),
                              ifelse(WT_spo13m2_fc>1.5 & WT_spo13m2_pval < 0.05,"DECR",
                                  ifelse(WT_spo13m2_fc<(1/1.5) & WT_spo13m2_pval < 0.05,"INCR","NC")),"NC")) %>%
    mutate(spo13_spo13m2_sig=ifelse(is.finite(spo13_spo13m2_fc)&is.finite(spo13_spo13m2_pval),
                              ifelse(spo13_spo13m2_fc>1.5 & WT_spo13m2_pval < 0.05,"INCR",
                                  ifelse(WT_spo13m2_fc<(1/1.5) & WT_spo13m2_pval < 0.05,"DECR","NC")),"NC")) %>%
    # adjust so factor levels are all the same
     mutate(spo13_WT_sig=factor(spo13_WT_sig,levels=c("NC","INCR","DECR"))) %>%
     mutate(spo13m2_WT_sig=factor(spo13m2_WT_sig,levels=c("NC","INCR","DECR"))) %>%
     mutate(spo13_spo13m2_sig=factor(spo13_spo13m2_sig,levels=c("NC","INCR","DECR")))

```

# Indicate MVs
```{r,echo=F,message=F,warning=F}

# nona_norm.tmt.cols[c(1,4,7,10)] # WT
# nona_norm.tmt.cols[c(2,5,8)] # spo13
# nona_norm.tmt.cols[c(3,6,9)] # spo13-m2

protg <- protg %>%
    mutate(WT.3reps=apply(.[,nona_norm.tmt.cols[c(1,4,7,10)]],1,function(x) sum(x>0)>=3)) %>% # must be detected in 3/4 reps
    mutate(spo13.3reps=apply(.[,nona_norm.tmt.cols[c(2,5,8)]],1,function(x) sum(x>0)==3)) %>% # must be detected in 3 reps
    mutate(spo13m2.3reps=apply(.[,nona_norm.tmt.cols[c(3,6,9)]],1,function(x) sum(x>0)==3)) %>% # must be detected in 3 reps
    mutate(WT.2reps=apply(.[,nona_norm.tmt.cols[c(1,4,7,10)]],1,function(x) sum(x>0)>=2)) %>% # must be detected in 2/4 reps
    mutate(spo13.2reps=apply(.[,nona_norm.tmt.cols[c(2,5,8)]],1,function(x) sum(x>0)>=2)) %>% # must be detected in 2 reps
    mutate(spo13m2.2reps=apply(.[,nona_norm.tmt.cols[c(3,6,9)]],1,function(x) sum(x>0)>=2)) %>% # must be detected in 2 reps
    mutate(WT.1reps=apply(.[,nona_norm.tmt.cols[c(1,4,7,10)]],1,function(x) sum(x>0)>=1)) %>% # must be detected in 1/4 reps
    mutate(spo13.1reps=apply(.[,nona_norm.tmt.cols[c(2,5,8)]],1,function(x) sum(x>0)>=1)) %>% # must be detected in 1 reps
    mutate(spo13m2.1reps=apply(.[,nona_norm.tmt.cols[c(3,6,9)]],1,function(x) sum(x>0)>=1)) # must be detected in 1 reps

#protg %>% filter(WT.3reps==T&spo13.3reps==T&spo13m2.3reps==T) %>% nrow() #3960 proteins detected in 3 reps of all strains

# filter to found in 3 reps of all strains
protg_3reps <- protg %>% filter(WT.3reps==T & spo13.3reps==T & spo13m2.3reps==T) #3960
                
# Indicate MVs in phosphos
phosphos <- phosphos %>%
    mutate(WT.3reps=apply(.[,nona_phos.stoic.cols[c(1,4,7,10)]],1,function(x) sum(x>0)>=3)) %>% # must be detected in 3/4 reps
    mutate(spo13.3reps=apply(.[,nona_phos.stoic.cols[c(2,5,8)]],1,function(x) sum(x>0)==3)) %>% # must be detected in 3 reps
    mutate(spo13m2.3reps=apply(.[,nona_phos.stoic.cols[c(3,6,9)]],1,function(x) sum(x>0)==3)) %>% # must be detected in 3 reps
mutate(WT.2reps=apply(.[,nona_phos.stoic.cols[c(1,4,7,10)]],1,function(x) sum(x>0)>=2)) %>% # must be detected in 2/4 reps
    mutate(spo13.2reps=apply(.[,nona_phos.stoic.cols[c(2,5,8)]],1,function(x) sum(x>0)>=2)) %>% # must be detected in 2 reps
    mutate(spo13m2.2reps=apply(.[,nona_phos.stoic.cols[c(3,6,9)]],1,function(x) sum(x>0)>=2)) %>% # must be detected in 2 reps
    mutate(WT.1reps=apply(.[,nona_phos.stoic.cols[c(1,4,7,10)]],1,function(x) sum(x>0)>=1)) %>% # must be detected in 1/4 reps
    mutate(spo13.1reps=apply(.[,nona_phos.stoic.cols[c(2,5,8)]],1,function(x) sum(x>0)>=1)) %>% # must be detected in 1 reps
    mutate(spo13m2.1reps=apply(.[,nona_phos.stoic.cols[c(3,6,9)]],1,function(x) sum(x>0)>=1)) # must be detected in 1 reps

    
# phosphos %>% filter(WT.3reps==T&spo13.3reps==T&spo13m2.3reps==T) %>% nrow() #8421 sites found in 3 reps of all strains
# phosphos %>% filter(WT.2reps==T&spo13.2reps==T&spo13m2.2reps==T) %>% nrow() #8770 sites found in 2 reps of all strains

# filter to found in 3 reps of all strains
phosphos_3reps <- phosphos %>% filter(WT.3reps==T & spo13.3reps==T & spo13m2.3reps==T) # 8421

# filter to found in 2/3 reps of each strains
phosphos_2reps <- phosphos %>% filter(WT.2reps==T & spo13.2reps==T & spo13m2.2reps==T) # 8770

# plot of things detected in 3 reps
# use columnss where Zeros are filled as NAs so they are ignored when calculating spread
boxplot(log2(protg_3reps[,norm.tmt.cols]),main="Detected in 3 reps of all strains",ylab="log2 intensity")
boxplot(log2(phosphos_3reps[,phos.stoic.cols]),main="Detected in 3 reps of all strains",ylab="log2 intensity")

# phosphos filter to high localization score
phosphos_3reps_loc <- phosphos_3reps %>%
  mutate(high.localiz.score=Localization.prob>0.75) %>% 
    filter(high.localiz.score==T) #6927

phosphos_2reps_loc <- phosphos_2reps %>%
  mutate(high.localiz.score=Localization.prob>0.75) %>% 
    filter(high.localiz.score==T) #7175

# phosphos filter to only include rows with at least 1/10 >0 observation in nona_phos.stoic.cols ___1 (this excludes ___2 and ___3 sites)
# important because it affects the total of motif matching sites


```

# Motif logos ALL SITES #D
```{r,echo=F,message=F,warning=F}

# not ssure what to make of MDS plot
# plotMDS(log2(phosphos[,phos.stoic.cols]), main = "phos.stoic",col = c(rep(c("red","green","blue"),3),"red"))

# all sites in each strain 

# WT
# ggseqlogo(substr(phosphos %>%
#     filter(WT.3reps==T) %>%
#     select(Sequence.window) %>% unlist(),
#     11,21),method="prob") +
#     ggtitle("WT all sites detected 3/3 reps")+
#     theme(legend.position="none")+
#     scale_x_continuous(breaks=1:11,labels=-5:5)
# 
# # spo13
# ggseqlogo(substr(phosphos %>%
#     filter(spo13.3reps==T) %>%
#     select(Sequence.window) %>% unlist(),
#     11,21),method="prob") +
#     ggtitle("spo13 all sites detected 3/3 reps")+
#     theme(legend.position="none")+
#     scale_x_continuous(breaks=1:11,labels=-5:5)
# 
# # spo13-m2
# ggseqlogo(substr(phosphos %>%
#     filter(spo13m2.3reps==T) %>%
#     select(Sequence.window) %>% unlist(),
#     11,21),method="prob") +
#     ggtitle("spo13-m2 all sites detected 3/3 reps")+
#     theme(legend.position="none")+
#     scale_x_continuous(breaks=1:11,labels=-5:5)

# all look the same.
# 
# how to draw out important differencess between strains?
# stats to call sig diff between strains


# you can see that the intensity is different in each different sample, within strain as well
# phosphos %>%
#     filter(Gene.name=="CDC5") %>%
#     select(phos.stoic.cols,gene.name_site) %>%
#     pivot_longer(-gene.name_site,names_to="sample",values_to="intensity",names_prefix="stoic_") %>%
#     ggplot(aes(x=sample,y=intensity),group=gene.name_site)+
#     stat_summary(aes(y=intensity,group=gene.name_site,color=gene.name_site),fun="median",geom="line",linewidth=1)+
#     theme_classic()+
#   theme(axis.text.x = element_text(angle=90,vjust=0.6))



```


# filter to sig
```{r,echo=F,message=F,warning=F}

# separate dfs for each type of comparison sig
protg_3reps_spo13_WT_sig <- protg_3reps %>%
    filter(spo13_WT_sig!="NC")

protg_3reps_spo13m2_WT_sig <- protg_3reps %>%
    filter(spo13m2_WT_sig!="NC")

protg_3reps_spo13_spo13m2_sig <- protg_3reps %>%
    filter(spo13_spo13m2_sig!="NC")

# phosphos 3 reps
phosphos_3reps_spo13_WT_sig <- phosphos_3reps_loc %>%
    filter(spo13_WT_sig!="NC")

phosphos_3reps_spo13m2_WT_sig <- phosphos_3reps_loc %>%
    filter(spo13m2_WT_sig!="NC")

phosphos_3reps_spo13_spo13m2_sig <- phosphos_3reps_loc %>%
    filter(spo13_spo13m2_sig!="NC")

```

# General numbers plots
```{r,echo=F,message=F,warning=F}

# PROTEINS

# boxplot of intensities in each sample
# Zeros are NAs in norm.tmt.cols
# log2(NA) is non-finite so is not included in boxplot
# if nona_norm.tmt.cols where zeros are zeros is used, still the zeros are not plotted because log2(0)=-Inf

protg_int_boxplot<-protg %>%
    select(all_of(norm.tmt.cols)) %>%
  pivot_longer(cols=all_of(norm.tmt.cols),names_to="sample",values_to="intensity",names_prefix="norm_") %>% select(sample,intensity) %>%
  ggplot(aes(x=fct_inorder(sample),y=log2(intensity),fill=sample)) +
  geom_boxplot(aes(fill=sample,alpha=0.2),position="dodge",outlier.size = 0.25, size = 0.25)+
  theme_classic()+
  labs(y="log2 intensity",x="")+
  ggtitle("protg intensity")+
theme(axis.text.x = element_text(angle=90,vjust=0.6,size=rel(1.5)),legend.position="none",axis.text.y=element_text(size=rel(1.5)),axis.title=element_text(size=rel(1.5)),plot.title=element_text(size=rel(2)))+
  coord_flip()

#barplot of numbers of detections (proteins) in each sample
protg_count_cols<-paste0(nona_norm.tmt.cols,"_count")

protg_per_samp_bar<-protg %>%
    mutate(across(all_of(nona_norm.tmt.cols),function(x) sum(x>0),.names = "{.col}_count")) %>%
    select(all_of(protg_count_cols)) %>%
    head(1) %>%
    pivot_longer(cols=protg_count_cols,values_to="number",names_to="time",names_prefix="nona_norm_") %>%
    mutate(time=as.factor(gsub("_count","",time))) %>%
   mutate(time=factor(fct_inorder(time),levels=c(raw_cols[1],raw_cols[6:10],raw_cols[2:5]))) %>% # matching color order of TC plots
  ggplot(aes(x=fct_inorder(time),y=number))+
  geom_bar(aes(fill=time),stat="identity")+
  geom_text(aes(label=number),vjust=0.5,hjust=1.3)+
  theme_classic()+
  theme(legend.position="none")+
  scale_y_continuous(expand=expansion(mult=c(0,0.1)),limits=c(0,4200))+
  labs(y="",x="",title="proteins per sample")+
  coord_flip()

    
# barplot number of proteins in 1/2/3 replicates of each sample
num_reps_cols<-grep("reps",colnames(protg),value=T)
reps_count_cols<-paste0(num_reps_cols,"_count")

# note colors are no longer that order but it's not worth it to mess about with that now
protg_per_rep_cum_bar<-protg %>%
    mutate(across(all_of(num_reps_cols),function(x) sum(x), .names= "{.col}_count")) %>%
    select(all_of(reps_count_cols)) %>%
    head(1) %>%
    pivot_longer(cols=reps_count_cols,values_to="number",names_to="sample") %>%
    mutate(sample=gsub("_count","",sample)) %>%
   #mutate(sample=factor(sample,levels=c(raw_cols[1],raw_cols[6:10],raw_cols[2:5]))) %>%
  ggplot(aes(x=fct_inorder(sample),y=number))+
  geom_bar(aes(fill=sample),stat="identity")+
  geom_text(aes(label=number),vjust=0.5,hjust=1.3)+
  theme_classic()+
  theme(legend.position="none")+
  scale_y_continuous(expand=expansion(mult=c(0,0.1)),limits=c(0,4200))+
  labs(y="",x="",title="cumulative number of proteins in replicates")+
  coord_flip()

# number of proteins in all 3 strains in 3/2/1 reps
all_strains_reps_cols<-c("all_strains_3reps","all_strains_2reps","all_strains_1reps")
all_strains_reps_cols_count<-paste0(all_strains_reps_cols,"_count")

protg_all_strains_cum_bar<-protg %>%
    mutate(all_strains_3reps=WT.3reps&spo13.3reps&spo13m2.3reps) %>%
    mutate(all_strains_2reps=WT.2reps&spo13.2reps&spo13m2.2reps) %>%
    mutate(all_strains_1reps=WT.1reps&spo13.1reps&spo13m2.1reps) %>%
    select(all_of(all_strains_reps_cols)) %>%
    mutate(across(all_of(all_strains_reps_cols),function(x) sum(x),.names="{.col}_count")) %>%
    select(all_of(all_strains_reps_cols_count)) %>%
    head(1) %>%
    pivot_longer(cols=all_of(all_strains_reps_cols_count),values_to="number",names_to="sample") %>%
    mutate(sample=gsub("_count","",sample)) %>%
   #mutate(sample=factor(sample,levels=c(raw_cols[1],raw_cols[6:10],raw_cols[2:5]))) %>%
  ggplot(aes(x=fct_inorder(sample),y=number))+
  geom_bar(aes(fill=sample),stat="identity")+
  geom_text(aes(label=number),vjust=0.5,hjust=1.3)+
  theme_classic()+
  theme(legend.position="none")+
  scale_y_continuous(expand=expansion(mult=c(0,0.1)),limits=c(0,4000))+
  labs(y="",x="",title="cumulative number of proteins in replicates")+
  coord_flip()

    
    
### PHOSPHO-SITES ####
# boxplot of intensities in each sample
# Zeros are NAs in norm.tmt.cols
# log2(NA) is non-finite so is not included in boxplot
# if nona_norm.tmt.cols where zeros are zeros is used, still the zeros are not plotted because log2(0)=-Inf

phos_int_boxplot<-phosphos %>%
    mutate(high.localiz.score=Localization.prob>0.75) %>% 
    filter(high.localiz.score==T) %>%
    select(all_of(phos.stoic.cols)) %>%
  pivot_longer(cols=all_of(phos.stoic.cols),names_to="sample",values_to="intensity",names_prefix="stoic_") %>% select(sample,intensity) %>%
  ggplot(aes(x=fct_inorder(sample),y=log2(intensity),fill=sample)) +
  geom_boxplot(aes(fill=sample,alpha=0.2),position="dodge",outlier.size = 0.25, size = 0.25)+
  theme_classic()+
  labs(y="log2 intensity",x="")+
  ggtitle("phospho-sites intensity")+
    theme(axis.text.x = element_text(angle=90,vjust=0.6,size=rel(1.5)),legend.position="none",axis.text.y=element_text(size=rel(1.5)),axis.title=element_text(size=rel(1.5)),plot.title=element_text(size=rel(2)))+
  coord_flip()

#barplot of numbers of detections (sites) in each sample
phos_count_cols<-paste0(nona_phos.stoic.cols,"_count")

phos_per_samp_bar<-phosphos %>%
    mutate(high.localiz.score=Localization.prob>0.75) %>% 
    filter(high.localiz.score==T) %>%
    mutate(across(all_of(nona_phos.stoic.cols),function(x) sum(x>0),.names = "{.col}_count")) %>%
    select(all_of(phos_count_cols)) %>%
    head(1) %>%
    pivot_longer(cols=phos_count_cols,values_to="number",names_to="time",names_prefix="nona_stoic_") %>%
   mutate(time=as.factor(gsub("_count","",time))) %>%
   mutate(time=factor(fct_inorder(time),levels=c(raw_cols[1],raw_cols[6:10],raw_cols[2:5]))) %>% # matching color order of TC plots
  ggplot(aes(x=fct_inorder(time),y=number))+
  geom_bar(aes(fill=time),stat="identity")+
  geom_text(aes(label=number),vjust=0.5,hjust=1.3)+
  theme_classic()+
  theme(legend.position="none")+
  scale_y_continuous(expand=expansion(mult=c(0,0.2)),limits=c(0,7500))+
  labs(y="",x="",title="sites per sample")+
  coord_flip()
    
# barplot number of proteins in 1/2/3 replicates of each sample
num_reps_cols_phos<-grep("reps",colnames(phosphos),value=T)
reps_count_cols_phos<-paste0(num_reps_cols_phos,"_count")

# note colors are no longer that order but it's not worth it to mess about with that now
phos_per_rep_cum_bar<-phosphos %>%
    mutate(high.localiz.score=Localization.prob>0.75) %>% 
    filter(high.localiz.score==T) %>%
    mutate(across(all_of(num_reps_cols_phos),function(x) sum(x), .names= "{.col}_count")) %>%
    select(all_of(reps_count_cols_phos)) %>%
    head(1) %>%
    pivot_longer(cols=reps_count_cols_phos,values_to="number",names_to="sample") %>%
    mutate(sample=gsub("_count","",sample)) %>%
   #mutate(sample=factor(sample,levels=c(raw_cols[1],raw_cols[6:10],raw_cols[2:5]))) %>%
  ggplot(aes(x=fct_inorder(sample),y=number))+
  geom_bar(aes(fill=sample),stat="identity")+
  geom_text(aes(label=number),vjust=0.5,hjust=1.3)+
  theme_classic()+
  theme(legend.position="none")+
  scale_y_continuous(expand=expansion(mult=c(0,0.2)),limits=c(0,7500))+
  labs(y="",x="",title="cumulative number of sites in replicates")+
  coord_flip()

# number of sites in all 3 strains in 3/2/1 reps
all_strains_reps_cols<-c("all_strains_3reps","all_strains_2reps","all_strains_1reps")
all_strains_reps_cols_count<-paste0(all_strains_reps_cols,"_count")

phos_all_strains_cum_bar<-phosphos %>%
    mutate(high.localiz.score=Localization.prob>0.75) %>% 
    filter(high.localiz.score==T) %>%
    mutate(all_strains_3reps=WT.3reps&spo13.3reps&spo13m2.3reps) %>%
    mutate(all_strains_2reps=WT.2reps&spo13.2reps&spo13m2.2reps) %>%
    mutate(all_strains_1reps=WT.1reps&spo13.1reps&spo13m2.1reps) %>%
    select(all_of(all_strains_reps_cols)) %>%
    mutate(across(all_of(all_strains_reps_cols),function(x) sum(x),.names="{.col}_count")) %>%
    select(all_of(all_strains_reps_cols_count)) %>%
    head(1) %>%
    pivot_longer(cols=all_of(all_strains_reps_cols_count),values_to="number",names_to="sample") %>%
    mutate(sample=gsub("_count","",sample)) %>%
   #mutate(sample=factor(sample,levels=c(raw_cols[1],raw_cols[6:10],raw_cols[2:5]))) %>%
  ggplot(aes(x=fct_inorder(sample),y=number))+
  geom_bar(aes(fill=sample),stat="identity")+
  geom_text(aes(label=number),vjust=0.5,hjust=1.3)+
  theme_classic()+
  theme(legend.position="none")+
  scale_y_continuous(expand=expansion(mult=c(0,0.1)),limits=c(0,7500))+
  labs(y="",x="",title="cumulative number of sites in replicates")+
  coord_flip()

print_plot(protg_int_boxplot,
           "Exp40E_protg_int_boxplot.pdf",6,5)

print_plot(protg_per_samp_bar,
           "Exp40E_protg_per_samp_bar.pdf",6,5)

print_plot(protg_per_rep_cum_bar,
           "Exp40E_protg_per_rep_cum_bar.pdf",6,5)

print_plot(protg_all_strains_cum_bar,
           "Exp40E_protg_all_strains_cum_bar.pdf",6,5)

print_plot(phos_int_boxplot,
           "Exp40E_phos_int_boxplot.pdf",6,5)

print_plot(phos_per_samp_bar,
           "Exp40E_phos_per_samp_bar.pdf",6,5)

print_plot(phos_per_rep_cum_bar,
           "Exp40E_phos_per_rep_cum_bar.pdf",6,5)

print_plot(phos_all_strains_cum_bar,
           "Exp40E_phos_all_strains_cum_bar.pdf",6,5)

```


# pie charts of sig changes in each comparison
```{r,echo=F,message=F,warning=F}


# protg WT v spo13
protg_spo13_WT_sig_pie <- protg_3reps %>% 
    group_by(spo13_WT_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13_WT_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I spo13 v WT proteins")+
    theme(legend.title=element_blank())

# protg WT v spo13m2
protg_spo13m2_WT_sig_pie <- protg_3reps %>% 
    group_by(spo13m2_WT_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13m2_WT_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I spo13m2 v WT proteins")+
    theme(legend.title=element_blank())

# protg spo13 v spo13m2
protg_spo13_spo13m2_sig_pie <- protg_3reps %>% 
    group_by(spo13_spo13m2_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13_spo13m2_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I spo13 v spo13m2 proteins")+
    theme(legend.title=element_blank())

# print_plot(protg_WT_spo13_sig_pie,"protg_WT_spo13_sig_pie.pdf",5,5)
# print_plot(protg_WT_spo13m2_sig_pie,"protg_WT_spo13m2_sig_pie.pdf",5,5)
# print_plot(protg_spo13_spo13m2_sig_pie,"protg_spo13_spo13m2_sig_pie.pdf",5,5)

# phosphos WT v spo13
# 3 reps detected sites ##########
phosphos_spo13_WT_sig_pie <- phosphos_3reps_loc %>% 
    group_by(spo13_WT_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13_WT_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I spo13 v WT sites")+
    theme(legend.title=element_blank())

# phosphos WT v spo13m2
phosphos_spo13m2_WT_sig_pie <- phosphos_3reps_loc %>% 
    group_by(spo13m2_WT_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13m2_WT_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I spo13m2 v WT sites")+
    theme(legend.title=element_blank())

# phosphos spo13 v spo13m2
phosphos_spo13_spo13m2_sig_pie <- phosphos_3reps_loc %>% 
    group_by(spo13_spo13m2_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13_spo13m2_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I spo13 v spo13m2 sites")+
    theme(legend.title=element_blank())


# print all pies in R  # only 3 reps
# protg_WT_spo13_sig_pie
# protg_WT_spo13m2_sig_pie
# protg_spo13_spo13m2_sig_pie
# phosphos_3reps_WT_spo13_sig_pie
# phosphos_3reps_WT_spo13m2_sig_pie
# phosphos_3reps_spo13_spo13m2_sig_pie



#library(patchwork)

# all 3 pies in 1 graphic
# protg_spo13_WT_sig_pie
# +protg_spo13m2_WT_sig_pie+protg_spo13_spo13m2_sig_pie

print_plot(protg_spo13_WT_sig_pie+protg_spo13m2_WT_sig_pie+protg_spo13_spo13m2_sig_pie,
           "protg_sig_cat_pies.pdf",12,4)
print_plot(phosphos_spo13_WT_sig_pie+phosphos_spo13m2_WT_sig_pie+phosphos_spo13_spo13m2_sig_pie,
           "phosphos_sig_cat_pies.pdf",12,4)


```

# MOTIFS of all sigdiff sites
```{r,echo=F,message=F,warning=F}

# all sig sites (no INCR/DECR division)
# WT v spo13 3 reps
WT_spo13_3reps_allsig_logo<-ggseqlogo(substr(phosphos_3reps_loc %>% filter(spo13_WT_sig!="NC") %>% select(Sequence.window) %>% unlist(),11,21),method="prob") +
    ggtitle(paste0("spo13 v WT sigdiff sites, n=",phosphos_3reps_loc %>% filter(spo13_WT_sig!="NC") %>% nrow()))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# WT v spo13m2 3 reps
WT_spo13m2_3reps_allsig_logo<-ggseqlogo(substr(phosphos_3reps_loc %>% filter(spo13m2_WT_sig!="NC") %>% select(Sequence.window) %>% unlist(),11,21),method="prob") +
    ggtitle(paste0("spo13m2 v WT sigdiff sites, n=",phosphos_3reps_loc %>% filter(spo13m2_WT_sig!="NC") %>% nrow()))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# spo13 v spo13m2 3 reps
spo13_spo13m2_3reps_allsig_logo<-ggseqlogo(substr(phosphos_3reps_loc %>% filter(spo13_spo13m2_sig!="NC") %>% select(Sequence.window) %>% unlist(),11,21),method="prob") +
    ggtitle(paste0("spo13 v spo13m2 sigdiff sites, n=",phosphos_3reps_loc %>% filter(spo13_spo13m2_sig!="NC") %>% nrow()))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

#   print all logos in R
# WT_spo13_3reps_allsig_logo
# WT_spo13m2_3reps_allsig_logo
# spo13_spo13m2_3reps_allsig_logo

# print logos to pdf
print_plot(WT_spo13_3reps_allsig_logo,"WT_spo13_3reps_allsig_logo.pdf",6,4)
print_plot(WT_spo13m2_3reps_allsig_logo,"WT_spo13m2_3reps_allsig_logo.pdf",6,4)
print_plot(spo13_spo13m2_3reps_allsig_logo,"spo13_spo13m2_3reps_allsig_logo.pdf",6,4)
```

# sigcat seqs excel
```{r,echo=F,message=F,warning=F}
# export seq lists for each category

# Seq Lists used to make IceLogos
# single sheet with different columns for each sigdiff category

phos_sig_cat_seq_dfs<-list()
phos_sig_cat_seq_dfs[[1]]<-phosphos_3reps_loc %>%
   mutate(Sequence.window_5=substr(Sequence.window,11,21)) %>%
   # mutate(spo13_WT_sig=factor(spo13_WT_sig,levels=c("NC","INCR","DECR"))) %>%
    arrange(spo13_WT_sig) %>%
    group_by(spo13_WT_sig) %>%
    mutate(id=row_number()) %>%
    pivot_wider(names_from=spo13_WT_sig,values_from=Sequence.window_5,id_cols=id) %>%
    select(-id)
phos_sig_cat_seq_dfs[[2]]<-phosphos_3reps_loc %>%
   mutate(Sequence.window_5=substr(Sequence.window,11,21)) %>%
   # mutate(spo13m2_WT_sig=factor(spo13m2_WT_sig,levels=c("NC","INCR","DECR"))) %>%
    arrange(spo13m2_WT_sig) %>%
    group_by(spo13m2_WT_sig) %>%
    mutate(id=row_number()) %>%
    pivot_wider(names_from=spo13m2_WT_sig,values_from=Sequence.window_5,id_cols=id) %>%
    select(-id)
phos_sig_cat_seq_dfs[[3]]<-phosphos_3reps_loc %>%
   mutate(Sequence.window_5=substr(Sequence.window,11,21)) %>%
   #mutate(spo13_spo13m2_sig=factor(spo13_spo13m2_sig,levels=c("NC","INCR","DECR"))) %>%
    arrange(spo13_spo13m2_sig) %>%
    group_by(spo13_spo13m2_sig) %>%
    mutate(id=row_number()) %>%
    pivot_wider(names_from=spo13_spo13m2_sig,values_from=Sequence.window_5,id_cols=id) %>%
    select(-id)

names(phos_sig_cat_seq_dfs)<-c("spo13_WT_sig","spo13m2_WT_sig","spo13_spo13m2_sig")

write.xlsx(phos_sig_cat_seq_dfs,file="MetaphaseI_sig_cat_seqs.xlsx")

```

# MOTIFS of INCR/DECR sites

```{r,echo=F,message=F,warning=F}

# INCR
# spo13 v WT
spo13_WT_INCR_logo<-ggseqlogo(substr(phosphos_3reps_loc %>% filter(spo13_WT_sig=="INCR") %>% select(Sequence.window) %>% unlist(),11,21),method="prob") +
    ggtitle(paste0("spo13 v WT INCR sites, n=",phosphos_3reps_loc %>% filter(spo13_WT_sig=="INCR") %>% nrow()))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# spo13m3 v WT
spo13m2_WT_INCR_logo<-ggseqlogo(substr(phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="INCR") %>% select(Sequence.window) %>% unlist(),11,21),method="prob") +
    ggtitle(paste0("spo13m2 v WT INCR sites, n=",phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="INCR") %>% nrow()))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# spo13 v spo13m2
spo13_spo13m2_INCR_logo<-ggseqlogo(substr(phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="INCR") %>% select(Sequence.window) %>% unlist(),11,21),method="prob") +
    ggtitle(paste0("spo13 v spo13m2 INCR sites, n=",phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="INCR") %>% nrow()))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# DECR
# spo13 v WT
spo13_WT_DECR_logo<-ggseqlogo(substr(phosphos_3reps_loc %>% filter(spo13_WT_sig=="DECR") %>% select(Sequence.window) %>% unlist(),11,21),method="prob") +
    ggtitle(paste0("spo13 v WT DECR sites, n=",phosphos_3reps_loc %>% filter(spo13_WT_sig=="DECR") %>% nrow()))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# spo13m2 v WT
spo13m2_WT_DECR_logo<-ggseqlogo(substr(phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="DECR") %>% select(Sequence.window) %>% unlist(),11,21),method="prob") +
    ggtitle(paste0("spo13m2 v WT DECR sites, n=",phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="DECR") %>% nrow()))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# spo13 v spo13m2
spo13_spo13m2_DECR_logo<-ggseqlogo(substr(phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="DECR") %>% select(Sequence.window) %>% unlist(),11,21),method="prob") +
    ggtitle(paste0("spo13 v spo13m2 DECR sites, n=",phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="DECR") %>% nrow()))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)
   
# print logos in R
# WT_spo13_3reps_INCR_logo
# WT_spo13m2_3reps_INCR_logo
# spo13_spo13m2_3reps_INCR_logo
# WT_spo13_3reps_DECR_logo
# WT_spo13m2_3reps_DECR_logo
# spo13_spo13m2_3reps_DECR_logo

# print logos to pdf
print_plot(spo13_WT_INCR_logo,"spo13_WT_INCR_logo.pdf",6,4)
print_plot(spo13m2_WT_INCR_logo,"spo13m2_WT_INCR_logo.pdf",6,4)
print_plot(spo13_spo13m2_INCR_logo,"spo13_spo13m2_INCR_logo.pdf",6,4)
print_plot(spo13_WT_DECR_logo,"spo13_WT_DECR_logo.pdf",6,4)
print_plot(spo13m2_WT_DECR_logo,"spo13m2_WT_DECR_logo.pdf",6,4)
print_plot(spo13_spo13m2_DECR_logo,"spo13_spo13m2_3reps_DECR_logo.pdf",6,4)

```

# Sub DEN.ST sites surroundings logos
```{r,echo=F,message=F,warning=F}

# All DEN POLO sites

# spo13 v WT
# all sig
spo13_WT_allsig_polo_logo<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_WT_sig!="NC") %>%
    select(Sequence.window) %>% unlist() %>%
    substr(.,11,21) %>%
    ggseqlogo(.,method="prob")+
    ggtitle(paste0("spo13 v WT all sig sites, n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_WT_sig!="NC"))))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# incr
spo13_WT_INCR_polo_logo<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_WT_sig=="INCR") %>%
    select(Sequence.window) %>% unlist() %>%
    substr(.,11,21) %>%
    ggseqlogo(.,method="prob")+
    ggtitle(paste0("spo13 v WT INCR sites, n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_WT_sig=="INCR"))))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# decr
spo13_WT_DECR_polo_logo<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_WT_sig=="DECR") %>%
    select(Sequence.window) %>% unlist() %>%
    substr(.,11,21) %>%
    ggseqlogo(.,method="prob")+
    ggtitle(paste0("spo13 v WT DECR sites, n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_WT_sig=="DECR"))))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# spo13m2 v WT ######
# all sig
spo13m2_WT_allsig_polo_logo<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13m2_WT_sig!="NC") %>%
    select(Sequence.window) %>% unlist() %>%
    substr(.,11,21) %>%
    ggseqlogo(.,method="prob")+
    ggtitle(paste0("spo13m2 v WT all sig sites, n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13m2_WT_sig!="NC"))))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# incr
spo13m2_WT_INCR_polo_logo<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13m2_WT_sig=="INCR") %>%
    select(Sequence.window) %>% unlist() %>%
    substr(.,11,21) %>%
    ggseqlogo(.,method="prob")+
    ggtitle(paste0("spo13m2 v WT INCR sites, n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13m2_WT_sig=="INCR"))))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# decr
spo13m2_WT_DECR_polo_logo<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13m2_WT_sig=="DECR") %>%
    select(Sequence.window) %>% unlist() %>%
    substr(.,11,21) %>%
    ggseqlogo(.,method="prob")+
    ggtitle(paste0("spo13m2 v WT DECR sites, n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13m2_WT_sig=="DECR"))))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# spo13 v spo13m2 ######
# all sig
spo13_spo13m2_allsig_polo_logo<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_spo13m2_sig!="NC") %>%
    select(Sequence.window) %>% unlist() %>%
    substr(.,11,21) %>%
    ggseqlogo(.,method="prob")+
    ggtitle(paste0("spo13 v spo13m2 all sig sites, n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_spo13m2_sig!="NC"))))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# incr
spo13_spo13m2_INCR_polo_logo<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_spo13m2_sig=="INCR") %>%
    select(Sequence.window) %>% unlist() %>%
    substr(.,11,21) %>%
    ggseqlogo(.,method="prob")+
    ggtitle(paste0("spo13 v spo13m2 INCR sites, n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_spo13m2_sig=="INCR"))))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# decr
spo13_spo13m2_DECR_polo_logo<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_spo13m2_sig=="DECR") %>%
    select(Sequence.window) %>% unlist() %>%
    substr(.,11,21) %>%
    ggseqlogo(.,method="prob")+
    ggtitle(paste0("spo13 v spo13m2 DECR sites, n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_spo13m2_sig=="DECR"))))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)


# print logos to pdf
# all 9 logos in 1 graphic (can be broken up in illustrator later)
print_plot((spo13_WT_allsig_polo_logo+spo13m2_WT_allsig_polo_logo+spo13_spo13m2_allsig_polo_logo)/
               (spo13_WT_INCR_polo_logo+spo13m2_WT_INCR_polo_logo+spo13_spo13m2_INCR_polo_logo)/
               (spo13_WT_DECR_polo_logo+spo13m2_WT_DECR_polo_logo+spo13_spo13m2_DECR_polo_logo),
           "DEN_Polo_sites_logos.pdf",14,8)

# export sub DEN-ST site seq lists

# Seq Lists used to make IceLogos
# single sheet with different columns for each sigdiff category

DEN.ST_phos_sig_cat_seq_dfs<-list()
DEN.ST_phos_sig_cat_seq_dfs[[1]]<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
   mutate(Sequence.window_5=substr(Sequence.window,11,21)) %>%
    arrange(spo13_WT_sig) %>%
    group_by(spo13_WT_sig) %>%
    mutate(id=row_number()) %>%
    pivot_wider(names_from=spo13_WT_sig,values_from=Sequence.window_5,id_cols=id) %>%
    select(-id)
DEN.ST_phos_sig_cat_seq_dfs[[2]]<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
   mutate(Sequence.window_5=substr(Sequence.window,11,21)) %>%
    arrange(spo13m2_WT_sig) %>%
    group_by(spo13m2_WT_sig) %>%
    mutate(id=row_number()) %>%
    pivot_wider(names_from=spo13m2_WT_sig,values_from=Sequence.window_5,id_cols=id) %>%
    select(-id)
DEN.ST_phos_sig_cat_seq_dfs[[3]]<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
   mutate(Sequence.window_5=substr(Sequence.window,11,21)) %>%
    arrange(spo13_spo13m2_sig) %>%
    group_by(spo13_spo13m2_sig) %>%
    mutate(id=row_number()) %>%
    pivot_wider(names_from=spo13_spo13m2_sig,values_from=Sequence.window_5,id_cols=id) %>%
    select(-id)

names(DEN.ST_phos_sig_cat_seq_dfs)<-c("spo13_WT_sig","spo13m2_WT_sig","spo13_spo13m2_sig")

write.xlsx(DEN.ST_phos_sig_cat_seq_dfs,file="MetaphaseI_sub_DEN.ST_sig_cat_seqs.xlsx")


# Pie charts of proportion of sig-cat sites that are canonical Polo motif

DEN.ST_phosphos_spo13_WT_sig_pie <- phosphos_3reps_loc %>% 
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    group_by(spo13_WT_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13_WT_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I [DEN].[ST]* spo13 v WT sites")+
    theme(legend.title=element_blank())

# phosphos WT v spo13m2
DEN.ST_phosphos_spo13m2_WT_sig_pie <- phosphos_3reps_loc %>% 
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    group_by(spo13m2_WT_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13m2_WT_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I [DEN].[ST]* spo13m2 v WT sites")+
    theme(legend.title=element_blank())

# phosphos spo13 v spo13m2
DEN.ST_phosphos_spo13_spo13m2_sig_pie <- phosphos_3reps_loc %>% 
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    group_by(spo13_spo13m2_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13_spo13m2_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I [DEN].[ST]* spo13 v spo13m2 sites")+
    theme(legend.title=element_blank())

print_plot(DEN.ST_phosphos_spo13_WT_sig_pie+DEN.ST_phosphos_spo13m2_WT_sig_pie+DEN.ST_phosphos_spo13_spo13m2_sig_pie,
           "DEN.ST_sig_cat_phosphos_pies.pdf",12,4)

```

# +1F in Polo motif Pies
```{r,echo=F,message=F,warning=F}

# what proportion of sig diff sites are DEN-STF with INCR/DECR cat

DEN.STF_phosphos_spo13_WT_sig_pie <- phosphos_3reps_loc %>% 
    filter(grepl(".............[DEN].[ST]F..............",Sequence.window)) %>%
    group_by(spo13_WT_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13_WT_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I [DEN].[ST]*F spo13 v WT sites")+
    theme(legend.title=element_blank())

# phosphos WT v spo13m2
DEN.STF_phosphos_spo13m2_WT_sig_pie <- phosphos_3reps_loc %>% 
    filter(grepl(".............[DEN].[ST]F..............",Sequence.window)) %>%
    group_by(spo13m2_WT_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13m2_WT_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I [DEN].[ST]*F spo13m2 v WT sites")+
    theme(legend.title=element_blank())

# phosphos spo13 v spo13m2
DEN.STF_phosphos_spo13_spo13m2_sig_pie <- phosphos_3reps_loc %>% 
    filter(grepl(".............[DEN].[ST]F..............",Sequence.window)) %>%
    group_by(spo13_spo13m2_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13_spo13m2_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I [DEN].[ST]*F spo13 v spo13m2 sites")+
    theme(legend.title=element_blank())

print_plot(DEN.STF_phosphos_spo13_WT_sig_pie+DEN.STF_phosphos_spo13m2_WT_sig_pie+DEN.STF_phosphos_spo13_spo13m2_sig_pie,
           "DEN.STF_sig_cat_phosphos_pies.pdf",12,4)


# of DEN sites, how many have +1F in each of comparisons
# all sites proportion
DEN_F_allsites_pie<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    mutate(motif=ifelse(grepl("...............[ST]F..............",Sequence.window),"F","no_F")) %>%
    group_by(motif) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=motif,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle(paste0("+1F in DEN motif all sites n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)))))+
    theme(legend.title=element_blank())

# spo13 v WT sigdiff
DEN_F_spo13_WT_sig_pie<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_WT_sig!="NC") %>%
    mutate(motif=ifelse(grepl("...............[ST]F..............",Sequence.window),"F","no_F")) %>%
    group_by(motif) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=motif,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle(paste0("+1F in DEN motif spo13 v WT sig n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>% filter(spo13_WT_sig!="NC"))))+
    theme(legend.title=element_blank())


# WT v spo13m2 sigdiff
DEN_F_spo13m2_WT_sig_pie<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13m2_WT_sig!="NC") %>%
   mutate(motif=ifelse(grepl("...............[ST]F..............",Sequence.window),"F","no_F")) %>%
    group_by(motif) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=motif,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle(paste0("+1F in DEN motif spo13m2 v WT sig n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>% filter(spo13m2_WT_sig!="NC"))))+
    theme(legend.title=element_blank())

# spo13 v spo13m2 sigdiff
DEN_F_spo13_spo13m2_sig_pie<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_spo13m2_sig!="NC") %>%
    mutate(motif=ifelse(grepl("...............[ST]F..............",Sequence.window),"F","no_F")) %>%
    group_by(motif) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=motif,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle(paste0("+1F in DEN motif spo13 v spo13m2 sig n=",nrow(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>% filter(spo13_spo13m2_sig!="NC"))))+
    theme(legend.title=element_blank())

# print to pdf
print_plot((DEN_F_allsites_pie)/(DEN_F_spo13_WT_sig_pie)/(DEN_F_spo13m2_WT_sig_pie)/
                (DEN_F_spo13_spo13m2_sig_pie),
           "DEN.STF_out_of_DEN_pies.pdf",5,10)



```

## Polo fisher test barplots
```{r,echo=F,message=F,warning=F}

fisher<-function(df1,df2,motif){
    total.df1 <- df1 %>% nrow() 
    total.df2 <- df2 %>% nrow()
    match.df1 <- df1 %>% filter(grepl(motif,Sequence.window)) %>% nrow()
    match.df2 <- df2  %>% filter(grepl(motif,Sequence.window)) %>% nrow()
    corr.mat<-matrix(c(match.df1,(total.df1-match.df1),match.df2,(total.df2-match.df2)),
                     nrow=2,
                     dimnames= list(c("match","no match"),
                                    c("df1","df2")))
    fisher.result<-fisher.test(corr.mat)
    
    corr.mat<-corr.mat %>% as.data.frame() %>%
    rbind(colSums(.)) %>%
    cbind(rowSums(.)) %>%
    rbind(perc_match=(.[1,]/.[3,])*100)
    
    rownames(corr.mat)[3]<-"col_totals"
    colnames(corr.mat)<-c("df1","df2","row_totals")
    
    corr.mat<-corr.mat %>%
        cbind("pval"=fisher.result$p.value)

    
    return(corr.mat)
}

library(ggsignif)

# note "total" in this case is sites with high loc score and detected in 9/10 ___1 TMT channels (all 3 strains 3/4 WT reps)

fisher_barplot<-function(df1,df2,motif,subset1,subset2,title){
    out_df<-fisher(df1,df2,motif) %>%
    tail(1) %>%
     mutate(stars=ifelse(pval<0.001,"***",
                      ifelse(pval<0.01,"**",
                             ifelse(pval<0.05,"*",NA)))) %>%
    select(df1,df2,pval,stars) %>%
    pivot_longer(-c(pval,stars),values_to="perc",names_to="sample") %>%
    mutate(sample=ifelse(grepl("df1",sample),subset1,subset2)) %>%
        mutate(sample=factor(sample,levels=c(subset1,subset2))) # have to make sure levels are consistent
        
    out_df %>%
    ggplot(aes(x=sample,y=perc,fill=sample))+
    geom_bar(aes(fill=sample),stat="identity")+
   geom_signif(comparisons = list(c(subset1,subset2)), 
              map_signif_level=TRUE,
              annotations = out_df$stars[1],
              size=0.25)+
    scale_y_continuous(expand=expansion(mult=c(0,0.2)),labels = label_number(accuracy=0.1))+
    theme_classic()+
    theme(axis.text.x = element_text(angle=90,vjust=0.6),legend.position="none",axis.text=element_text(size=rel(1)))+
    labs(y="percent matches",x="",title=title,,axis.line=element_line(linewidth=0.1))
}


# sig vs NC comparisons
# DEN sites 3 comparisons
spo13_WT_DEN_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_spo13_WT_sig,".............[DEN].[ST]...............","spo13_WT_NC","spo13_WT_sig","spo13 v WT [DEN].[ST]* sites")
spo13m2_WT_DEN_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_spo13m2_WT_sig,".............[DEN].[ST]...............","spo13m2_WT_NC","spo13m2_WT_sig","spo13m2 v WT [DEN].[ST]* sites")
spo13_spo13m2_DEN_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_spo13_spo13m2_sig,".............[DEN].[ST]...............","spo13_spo13m2_NC","spo13_spo13m2_sig","spo13 v spo13m2 [DEN].[ST]* sites")


# DEN.STF sites 3 comparisons
spo13_WT_DEN.STF_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_spo13_WT_sig,".............[DEN].[ST]F..............","spo13_WT_NC","spo13_WT_sig","spo13 v WT [DEN].[ST]*F sites")
spo13m2_WT_DEN.STF_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_spo13m2_WT_sig,".............[DEN].[ST]F..............","spo13m2_WT_NC","spo13m2_WT_sig","spo13m2 v WT [DEN].[ST]*F sites")
spo13_spo13m2_DEN.STF_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_spo13_spo13m2_sig,".............[DEN].[ST]F..............","spo13_spo13m2_NC","spo13_spo13m2_sig","spo13 v spo13m2 [DEN].[ST]*F sites")

print_plot(spo13_WT_DEN_sig_v_NC_fish_bar+spo13m2_WT_DEN_sig_v_NC_fish_bar+spo13_spo13m2_DEN_sig_v_NC_fish_bar,
           "DEN_fisher_sig_v_NC_barplot.pdf",13,8)

print_plot(spo13_WT_DEN.STF_sig_v_NC_fish_bar+spo13m2_WT_DEN.STF_sig_v_NC_fish_bar+spo13_spo13m2_DEN.STF_sig_v_NC_fish_bar,
           "DEN.STF_fisher_sig_v_NC_barplot.pdf",13,8)

# DECR vs NC comparisons
# DEN sites 3 comparisons
spo13_WT_DEN_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_WT_sig=="DECR"),".............[DEN].[ST]...............","spo13_WT_NC","spo13_WT_DECR","spo13 v WT [DEN].[ST]* sites")

spo13m2_WT_DEN_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="DECR"),".............[DEN].[ST]...............","spo13m2_WT_NC","spo13m2_WT_DECR","spo13m2 v WT [DEN].[ST]* sites")

spo13_spo13m2_DEN_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="DECR"),".............[DEN].[ST]...............","spo13_spo13m2_NC","spo13_spo13m2_DECR","spo13 v spo13m2 [DEN].[ST]* sites")

# DEN.STF DECR sites 3 comparisons
spo13_WT_DEN.STF_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_WT_sig=="DECR"),".............[DEN].[ST]F..............","spo13_WT_NC","spo13_WT_DECR","spo13 v WT [DEN].[ST]*F sites")

spo13m2_WT_DEN.STF_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="DECR"),".............[DEN].[ST]F..............","spo13m2_WT_NC","WT_spo13m2_DECR","spo13m2 v WT [DEN].[ST]*F sites")

spo13_spo13m2_DEN.STF_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="DECR"),".............[DEN].[ST]F..............","spo13_spo13m2_NC","spo13_spo13m2_DECR","spo13 v spo13m2 [DEN].[ST]*F sites")

print_plot(spo13_WT_DEN_DECR_v_NC_fish_bar+spo13m2_WT_DEN_DECR_v_NC_fish_bar+spo13_spo13m2_DEN_DECR_v_NC_fish_bar,
           "DEN_fisher_DECR_v_NC_barplot.pdf",13,8)

print_plot(spo13_WT_DEN.STF_DECR_v_NC_fish_bar+spo13m2_WT_DEN.STF_DECR_v_NC_fish_bar+spo13_spo13m2_DEN.STF_DECR_v_NC_fish_bar,
           "DEN.STF_fisher_DECR_v_NC_barplot.pdf",13,8)

```

## CDK site fisher test barplots
```{r,echo=F,message=F,warning=F}


# Pie charts of proportion of sig-cat sites that are min CDK SP/TP

STP_phosphos_spo13_WT_sig_pie <- phosphos_3reps_loc %>% 
    filter(grepl("...............[ST]P..............",Sequence.window)) %>%
    group_by(spo13_WT_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13_WT_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I [ST]*P spo13 v WT sites")+
    theme(legend.title=element_blank())


STP_phosphos_spo13m2_WT_sig_pie <- phosphos_3reps_loc %>% 
    filter(grepl("...............[ST]P..............",Sequence.window)) %>%
    group_by(spo13m2_WT_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13m2_WT_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I [ST]*P spo13m2 v WT sites")+
    theme(legend.title=element_blank())


STP_phosphos_spo13_spo13m2_sig_pie <- phosphos_3reps_loc %>% 
    filter(grepl("...............[ST]P..............",Sequence.window)) %>%
    group_by(spo13_spo13m2_sig) %>%
    summarize(n=n()) %>%
    ggplot(aes(x="",y=n,fill=spo13_spo13m2_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF"))+
    ggtitle("Metaphase I [ST]*P spo13 v spo13m2 sites")+
    theme(legend.title=element_blank())

print_plot(STP_phosphos_spo13_WT_sig_pie+STP_phosphos_spo13m2_WT_sig_pie+STP_phosphos_spo13_spo13m2_sig_pie,
           "STP_sig_cat_phosphos_pies.pdf",12,4)



######## sig vs NC comparisons #### 
########
# SP sites 3 comparisons
spo13_WT_SP_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_spo13_WT_sig,"...............[ST]P..............","spo13_WT_NC","spo13_WT_sig","spo13 v WT [ST]*P sites")
spo13m2_WT_SP_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_spo13m2_WT_sig,"...............[ST]P..............","spo13m2_WT_NC","spo13m2_WT_sig","spo13m2 v WT [ST]*P sites")
spo13_spo13m2_SP_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_spo13_spo13m2_sig,"...............[ST]P..............","spo13_spo13m2_NC","spo13_spo13m2_sig","spo13 v spo13m2 [ST]*P sites")

print_plot(spo13_WT_SP_sig_v_NC_fish_bar+spo13m2_WT_SP_sig_v_NC_fish_bar+spo13_spo13m2_SP_sig_v_NC_fish_bar,
           "SP_fisher_sig_v_NC_barplot.pdf",13,8)


#SP.KR sites 
spo13_WT_SP.KR_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_spo13_WT_sig,"...............[ST]P.[KR]............","spo13_WT_NC","spo13_WT_sig","spo13 v WT [ST]*P.[KR] sites")
spo13m2_WT_SP.KR_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_spo13m2_WT_sig,"...............[ST]P.[KR]............","spo13m2_WT_NC","spo13m2_WT_sig","spo13m2 v WT [ST]*P.[KR] sites")
spo13_spo13m2_SP.KR_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_spo13_spo13m2_sig,"...............[ST]P.[KR]............","spo13_spo13m2_NC","spo13_spo13m2_sig","spo13 v spo13m2 [ST]*P.[KR] sites")

print_plot(spo13_WT_SP.KR_sig_v_NC_fish_bar+spo13m2_WT_SP.KR_sig_v_NC_fish_bar+spo13_spo13m2_SP.KR_sig_v_NC_fish_bar,
           "SP.KR_fisher_sig_v_NC_barplot.pdf",13,8)


# # overlapping DEN and SP sites
# WT_spo13_DEN.SP_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(WT_spo13_sig=="NC"),phosphos_3reps_WT_spo13_sig,".............[DEN].[ST]P..............","WT_spo13_NC","WT_spo13_sig","WT v spo13 [DEN].[ST]P sites")
# WT_spo13m2_DEN.SP_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(WT_spo13m2_sig=="NC"),phosphos_3reps_WT_spo13m2_sig,".............[DEN].[ST]P..............","WT_spo13m2_NC","WT_spo13m2_sig","WT v spo13m2 [DEN].[ST]P sites")
# spo13_spo13m2_DEN.SP_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_spo13_spo13m2_sig,".............[DEN].[ST]P..............","spo13_spo13m2_NC","spo13_spo13m2_sig","spo13 v spo13m2 [DEN].[ST]P sites")
# 
# print_plot(WT_spo13_DEN.SP_sig_v_NC_fish_bar+WT_spo13m2_DEN.SP_sig_v_NC_fish_bar+spo13_spo13m2_DEN.SP_sig_v_NC_fish_bar,
#            "DEN.STP_fisher_sig_v_NC_barplot.pdf",13,8)

######## DECR vs NC comparisons #### 
########
# SP sites 3 comparisons
spo13_WT_SP_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_WT_sig=="DECR"),"...............[ST]P..............","spo13_WT_NC","spo13_WT_DECR","spo13 v WT [ST]*P sites")
spo13m2_WT_SP_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="DECR"),"...............[ST]P..............","spo13m2_WT_NC","spo13m2_WT_DECR","spo13m2 v WT [ST]*P sites")
spo13_spo13m2_SP_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="DECR"),"...............[ST]P..............","spo13_spo13m2_NC","spo13_spo13m2_DECR","spo13 v spo13m2 [ST]*P sites")

print_plot(spo13_WT_SP_DECR_v_NC_fish_bar+spo13m2_WT_SP_DECR_v_NC_fish_bar+spo13_spo13m2_SP_DECR_v_NC_fish_bar,
           "SP_fisher_DECR_v_NC_barplot.pdf",13,8)

#SP.KR sites 
spo13_WT_SP.KR_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_WT_sig=="DECR"),"...............[ST]P.[KR]............","spo13_WT_NC","spo13_WT_DECR","spo13 v WT [ST]*P.[KR] sites")
spo13m2_WT_SP.KR_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="DECR"),"...............[ST]P.[KR]............","spo13m2_WT_NC","spo13m2_WT_DECR","spo13m2 v WT [ST]*P.[KR] sites")
spo13_spo13m2_SP.KR_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="DECR"),"...............[ST]P.[KR]............","spo13_spo13m2_NC","spo13_spo13m2_DECR","spo13 v spo13m2 [ST]*P.[KR] sites")

print_plot(spo13_WT_SP.KR_DECR_v_NC_fish_bar+spo13m2_WT_SP.KR_DECR_v_NC_fish_bar+spo13_spo13m2_SP.KR_DECR_v_NC_fish_bar,
           "SP.KR_fisher_DECR_v_NC_barplot.pdf",13,8)


# # overlapping DEN and SP sites
# spo13_WT_DEN.SP_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_WT_sig=="DECR"),".............[DEN].[ST]P..............","spo13_WT_NC","spo13_WT_DECR","spo13 v WT [DEN].[ST]*P sites")
# spo13m2_WT_DEN.SP_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="DECR"),".............[DEN].[ST]P..............","spo13m2_WT_NC","spo13m2_WT_DECR","spo13m2 v WT [DEN].[ST]*P sites")
# spo13_spo13m2_DEN.SP_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="DECR"),".............[DEN].[ST]P..............","spo13_spo13m2_NC","spo13_spo13m2_DECR","spo13 v spo13m2 [DEN].[ST]*P sites")
# 
# print_plot(spo13_WT_DEN.SP_DECR_v_NC_fish_bar+spo13m2_WT_DEN.SP_DECR_v_NC_fish_bar+spo13_spo13m2_DEN.SP_DECR_v_NC_fish_bar,
#            "DEN.STP_fisher_DECR_v_NC_barplot.pdf",13,8)


```

## RK.ST/RK..ST sites fisher barplots
```{r,echo=F,message=F,warning=F}

# RK at -2 sites 3 comparisons
spo13_WT_RK.ST_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_spo13_WT_sig,".............[RK].[ST]...............","spo13_WT_NC","spo13_WT_sig","spo13 v WT [RK].[ST]* sites")
spo13m2_WT_RK.ST_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_spo13m2_WT_sig,".............[RK].[ST]...............","spo13m2_WT_NC","spo13m2_WT_sig","spo13m2 v WT [RK].[ST]* sites")
spo13_spo13m2_RK.ST_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_spo13_spo13m2_sig,".............[RK].[ST]...............","spo13_spo13m2_NC","spo13_spo13m2_sig","spo13 v spo13m2 [RK].[ST]* sites")

print_plot(spo13_WT_RK.ST_sig_v_NC_fish_bar+spo13m2_WT_RK.ST_sig_v_NC_fish_bar+spo13_spo13m2_RK.ST_sig_v_NC_fish_bar,
           "RK.ST_fisher_sig_v_NC_barplot.pdf",13,8)

# RK at -3 sites 3 comparisons
spo13_WT_RK..ST_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_spo13_WT_sig,"............[RK]..[ST]...............","spo13_WT_NC","spo13_WT_sig","spo13 v WT [RK]..[ST]* sites")
spo13m2_WT_RK..ST_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_spo13m2_WT_sig,"............[RK]..[ST]...............","spo13m2_WT_NC","spo13m2_WT_sig","spo13m2 v WT [RK]..[ST]* sites")
spo13_spo13m2_RK..ST_sig_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_spo13_spo13m2_sig,"............[RK]..[ST]...............","spo13_spo13m2_NC","spo13_spo13m2_sig","spo13 v spo13m2 [RK]..[ST]* sites")

print_plot(spo13_WT_RK..ST_sig_v_NC_fish_bar+spo13m2_WT_RK..ST_sig_v_NC_fish_bar+spo13_spo13m2_RK..ST_sig_v_NC_fish_bar,
           "RK..ST_fisher_sig_v_NC_barplot.pdf",13,8)


# INCR v NC 
# RK at -2
spo13_WT_RK.ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_WT_sig=="INCR"),".............[RK].[ST]...............","spo13_WT_NC","spo13_WT_INCR","spo13 v WT [RK].[ST]* sites")
spo13m2_WT_RK.ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="INCR"),".............[RK].[ST]...............","spo13m2_WT_NC","spo13m2_WT_INCR","spo13m2 v WT [RK].[ST]* sites")
spo13_spo13m2_RK.ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="INCR"),".............[RK].[ST]...............","spo13_spo13m2_NC","spo13_spo13m2_INCR","spo13 v spo13m2 [RK].[ST]* sites")

print_plot(spo13_WT_RK.ST_INCR_v_NC_fish_bar+spo13m2_WT_RK.ST_INCR_v_NC_fish_bar+spo13_spo13m2_RK.ST_INCR_v_NC_fish_bar,
           "RK.ST_fisher_INCR_v_NC_barplot.pdf",13,8)

# RK at -3
spo13_WT_RK..ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_WT_sig=="INCR"),"............[RK]..[ST]...............","spo13_WT_NC","spo13_WT_INCR","spo13 v WT [RK]..[ST]* sites")
spo13m2_WT_RK..ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="INCR"),"............[RK]..[ST]...............","spo13m2_WT_NC","spo13m2_WT_INCR","spo13m2 v WT [RK]..[ST]* sites")
spo13_spo13m2_RK..ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc%>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="INCR"),"............[RK]..[ST]...............","spo13_spo13m2_NC","spo13_spo13m2_INCR","spo13 v spo13m2 [RK]..[ST]* sites")

print_plot(spo13_WT_RK..ST_INCR_v_NC_fish_bar+spo13m2_WT_RK..ST_INCR_v_NC_fish_bar+spo13_spo13m2_RK..ST_INCR_v_NC_fish_bar,
           "RK..ST_fisher_INCR_v_NC_barplot.pdf",13,8)


# 
# # DEPLETION OF BASOPHILIC MOTIFS AMONG SIG INCR SITES
# # INCR v NC #####
# # [RK].ST
# WT_spo13_RK.ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>%
#                                                      filter(WT_spo13_sig=="NC"),phosphos_3reps_loc %>% filter(WT_spo13_sig=="INCR"),".............[RK].[ST]...............","WT_spo13_NC","WT_spo13_INCR","WT v spo13 [RK].[ST] sites")
# WT_spo13m2_RK.ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>%
#                                                      filter(WT_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(WT_spo13m2_sig=="INCR"),".............[RK].[ST]...............","WT_spo13m2_NC","WT_spo13m2_INCR","WT v spo13m2 [RK].[ST] sites")
# spo13_spo13m2_RK.ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>%
#                                                      filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="INCR"),".............[RK].[ST]...............","spo13_spo13m2_NC","spo13_spo13m2_INCR","spo13 v spo13m2 [RK].[ST] sites")
# 
# print_plot(WT_spo13_RK.ST_INCR_v_NC_fish_bar+WT_spo13m2_RK.ST_INCR_v_NC_fish_bar+spo13_spo13m2_RK.ST_INCR_v_NC_fish_bar,
#            "RK.ST_fisher_INCR_v_NC_barplot.pdf",13,8)
# 
# # [RK]..ST
# WT_spo13_RK..ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>%
#                                                      filter(WT_spo13_sig=="NC"),phosphos_3reps_loc %>% filter(WT_spo13_sig=="INCR"),"............[RK]..[ST]...............","WT_spo13_NC","WT_spo13_INCR","WT v spo13 [RK]..[ST] sites")
# WT_spo13m2_RK..ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>%
#                                                      filter(WT_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(WT_spo13m2_sig=="INCR"),"............[RK]..[ST]...............","WT_spo13m2_NC","WT_spo13m2_INCR","WT v spo13m2 [RK]..[ST] sites")
# spo13_spo13m2_RK..ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>%
#                                                      filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="INCR"),"............[RK]..[ST]...............","spo13_spo13m2_NC","spo13_spo13m2_INCR","spo13 v spo13m2 [RK]..[ST] sites")
# 
# print_plot(WT_spo13_RK..ST_INCR_v_NC_fish_bar+WT_spo13m2_RK..ST_INCR_v_NC_fish_bar+spo13_spo13m2_RK..ST_INCR_v_NC_fish_bar,
#            "RK..ST_fisher_INCR_v_NC_barplot.pdf",13,8)
# 
# # RKRK.ST motif
# WT_spo13_RKRK.ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(WT_spo13_sig=="NC"),phosphos_3reps_loc %>% filter(WT_spo13_sig=="INCR"),"............[RK][RK].[ST]...............","WT_spo13_NC","WT_spo13_INCR","WT v spo13 [RK][RK].[ST] sites")
# WT_spo13m2_RKRK.ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>%
#                                                          filter(WT_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(WT_spo13m2_sig=="INCR"),"............[RK][RK].[ST]...............","WT_spo13m2_NC","WT_spo13m2_INCR","WT v spo13m2 [RK][RK].[ST] sites")
# spo13_spo13m2_RKRK.ST_INCR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="INCR"),"............[RK][RK].[ST]...............","spo13_spo13m2_NC","spo13_spo13m2_INCR","spo13 v spo13m2 [RK][RK].[ST] sites")
# 
# print_plot(WT_spo13_RKRK.ST_INCR_v_NC_fish_bar+WT_spo13m2_RKRK.ST_INCR_v_NC_fish_bar+spo13_spo13m2_RKRK.ST_INCR_v_NC_fish_bar,
#            "RKRK.ST_fisher_INCR_v_NC_barplot.pdf",13,8)


```

## Polo sub-motifs fisher test barplots
```{r,echo=F,message=F,warning=F}

# +1 hydrophobic LIM or aromatic FY = [LIMFY]
# # DECR vs NC comparisons 
# DEN.[ST][LIMFY] sites 3 comparisons
spo13_WT_DEN.SThyd_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_WT_sig=="DECR"),".............[DEN].[ST]*[FMYIL]..............","spo13_WT_NC","spo13_WT_DECR","spo13 v WT [DEN].[ST]*[LIMFY] sites")
spo13m2_WT_DEN.SThyd_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="DECR"),".............[DEN].[ST]*[FMYIL]..............","spo13m2_WT_NC","spo13m2_WT_DECR","spo13m2 v WT [DEN].[ST]*[LIMFY] sites")
spo13_spo13m2_DEN.SThyd_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="DECR"),".............[DEN].[ST][FMYIL]..............","spo13_spo13m2_NC","spo13_spo13m2_DECR","spo13 v spo13m2 [DEN].[ST]*[LIMFY] sites")

print_plot(spo13_WT_DEN.SThyd_DECR_v_NC_fish_bar+spo13m2_WT_DEN.SThyd_DECR_v_NC_fish_bar+spo13_spo13m2_DEN.SThyd_DECR_v_NC_fish_bar,
           "DEN.SThyd_fisher_DECR_v_NC_barplot.pdf",13,8)

## PRK1/ARK1/AKL1 motif in spo13m2 INCR 
# PRK= [LIM].[ST]*G
# ARK1= [TS]*G
# AKL1=[LMI]..[QHM].[T]*[G]

# [DEN].[ST]*G motif
spo13_WT_DEN.STG_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_WT_sig=="DECR"),".............[DEN].[ST]G..............","spo13_WT_NC","spo13_WT_DECR","spo13 v WT [DEN].[ST]*G sites")
spo13m2_WT_DEN.STG_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="DECR"),".............[DEN].[ST]G..............","spo13m2_WT_NC","spo13m2_WT_DECR","spo13m2 v WT [DEN].[ST]*G sites")
spo13_spo13m2_DEN.STG_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="DECR"),".............[DEN].[ST]G..............","spo13_spo13m2_NC","spo13_spo13m2_DECR","spo13 v spo13m2 [DEN].[ST]*G sites")

print_plot(spo13_WT_DEN.STG_DECR_v_NC_fish_bar+spo13m2_WT_DEN.STG_DECR_v_NC_fish_bar+spo13_spo13m2_DEN.STG_DECR_v_NC_fish_bar,
           "DEN.STG_fisher_DECR_v_NC_barplot.pdf",13,8)

# AKL1=[LMI]..[QHM].[T]*[G] --- LIM at -4
# because I only see the +1G in DEN sites, retain DEN at -2
# [LIM]..[DEN].[ST]G -- LIM at -4
spo13_WT_LIM..DEN.STG_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_WT_sig=="DECR"),"..........[LIM]..[DEN].[ST]G..............","spo13_WT_NC","spo13_WT_DECR","spo13 v WT [LIM]..[DEN].[ST]*G sites")
spo13m2_WT_LIM..DEN.STG_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="NC"),phosphos_3reps_loc %>% filter(spo13m2_WT_sig=="DECR"),"..........[LIM]..[DEN].[ST]G..............","spo13m2_WT_NC","spo13m2_WT_DECR","spo13m2 v WT [LIM]..[DEN].[ST]*G sites")
spo13_spo13m2_LIM..DEN.STG_DECR_v_NC_fish_bar<-fisher_barplot(phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="NC"),phosphos_3reps_loc %>% filter(spo13_spo13m2_sig=="DECR"),"..........[LIM]..[DEN].[ST]G..............","spo13_spo13m2_NC","spo13_spo13m2_DECR","spo13 v spo13m2 [LIM]..[DEN].[ST]*G sites")


print_plot(spo13_WT_LIM..DEN.STG_DECR_v_NC_fish_bar+spo13m2_WT_LIM..DEN.STG_DECR_v_NC_fish_bar+spo13_spo13m2_LIM..DEN.STG_DECR_v_NC_fish_bar,
           "LIM..DEN.STG_fisher_DECR_v_NC_barplot.pdf",13,8) # no enrichment

```
   
# regular logo of sub-Polo motifs
```{r}

# doesn't look as good as icelogos
ggseqlogo(substr(phosphos_3reps_spo13_WT_sig %>% filter(spo13_WT_sig=="DECR") %>% filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>% select(Sequence.window) %>% unlist(),11,21),method="prob")+
    ggtitle(paste0("spo13 v WT DECR, n=",phosphos_3reps_spo13_WT_sig %>% filter(spo13_WT_sig=="DECR") %>% filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>% nrow()))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

```

## Non-Polo subset logo
```{r}

phosphos_3reps_loc %>%
    filter(!grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_WT_sig=="DECR") %>%
    select(Sequence.window) %>% unlist() %>%
    substr(.,11,21) %>%
    ggseqlogo(.,method="prob")+
    ggtitle(paste0("spo13 v WT non-[DEN]x[ST]* DECR sites, n=",nrow(phosphos_3reps_loc %>%
    filter(!grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13_WT_sig=="DECR"))))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

phosphos_3reps_loc %>%
    filter(!grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13m2_WT_sig=="DECR") %>%
    select(Sequence.window) %>% unlist() %>%
    substr(.,11,21) %>%
    ggseqlogo(.,method="prob")+
    ggtitle(paste0("spo13m2 v WT non-[DEN]x[ST]* DECR sites, n=",nrow(phosphos_3reps_loc %>%
    filter(!grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    filter(spo13m2_WT_sig=="DECR"))))+
    theme(legend.position="none")+
    scale_x_continuous(breaks=1:11,labels=-5:5)

# seq lists for icelogo
# DECR non-polo
# phosphos_3reps_loc %>%
#     filter(!grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
#     filter(spo13_WT_sig=="DECR") %>%
#     select(Sequence.window) %>% unlist() %>%
#     substr(.,11,21) %>%
#     write_clip()
# 
# # NC non-polo
# phosphos_3reps_loc %>%
#     filter(!grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
#     filter(spo13_WT_sig=="NC") %>%
#     select(Sequence.window) %>% unlist() %>%
#     substr(.,11,21) %>%
#     write_clip()
# 
# # DECR non-polo
# phosphos_3reps_loc %>%
#     filter(!grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
#     filter(spo13m2_WT_sig=="DECR") %>%
#     select(Sequence.window) %>% unlist() %>%
#     substr(.,11,21) %>%
#     write_clip()
# 
# # NC non-polo
# phosphos_3reps_loc %>%
#     filter(!grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
#     filter(spo13m2_WT_sig=="NC") %>%
#     select(Sequence.window) %>% unlist() %>%
#     substr(.,11,21) %>%
#     write_clip()


```


# Fisher barplots included in main figure
```{r}

# below first set of DECR v NC icelogos
print_plot(spo13_WT_DEN_DECR_v_NC_fish_bar+spo13m2_WT_DEN_DECR_v_NC_fish_bar+spo13_WT_SP_DECR_v_NC_fish_bar+spo13m2_WT_SP_DECR_v_NC_fish_bar,"main_fig_fisher_DECR_v_NC_barplot.pdf",8,13)

# below canonical Polo sub-motif logos
print_plot(spo13_WT_DEN.STF_DECR_v_NC_fish_bar+spo13m2_WT_DEN.STF_DECR_v_NC_fish_bar+spo13_WT_DEN.STG_DECR_v_NC_fish_bar+spo13m2_WT_DEN.STG_DECR_v_NC_fish_bar,"main_fig_sub_DEN_fisher_DECR_v_NC_barplot.pdf",8,13)

```


# Clustering of proteins most different
```{r,echo=F,message=F,warning=F}

# function to produce pheatmap of clustering results

get_clust_heatmap<-function(df,hclustdf,cols,clusternum,strain1,strain2,title){
    #cols<-gsub("nona_norm_","",cols)
    hclustdf.cutree<-cutree(hclustdf,k=clusternum)
  hclustdf.row_annots<-data.frame(cluster = as.factor(hclustdf.cutree))
  # strain.col_annots<-data.frame(strain=as.factor(c(rep("WT",10),rep("spo13",10))))
  # rownames(strain.col_annots)<-colnames(df[,meancols])
  rownames(hclustdf.row_annots)<-df$Gene.name
 rownames(df)<-df$Gene.name
 colnames(df[,cols])<-gsub("nona_norm_","",colnames(df[,cols]))
 
  clust.heatmap<-pheatmap(df[,cols], main=paste0(title," n=",nrow(df)),scale = 'row', clustering_method = "ward.D2",annotation_row=hclustdf.row_annots,cutree_rows = clusternum, show_rownames = T, show_colnames = T, cluster_cols = T,border_color = "NA",labels_col=gsub("nona_norm_","",colnames(df[,cols]))
                          )
  return(clust.heatmap)
}


# clustering heatmaps

protg_WT_cols<-grep("WT",nona_norm.tmt.cols,value=T)
protg_spo13_cols<-grep("spo13_",nona_norm.tmt.cols,value=T)
protg_spo13m2_cols<-grep("spo13m2",nona_norm.tmt.cols,value=T)

# spo13 v WT proteins
#hclust
protg_3reps_spo13_WT_sig.hclust<-hclust(dist(t(apply(as.matrix(protg_3reps_spo13_WT_sig[,c(protg_WT_cols,protg_spo13_cols)]),1,scale))),method="ward.D2")

# how many clusters are appropriate
wssplot(as.matrix(protg_3reps_spo13_WT_sig[,c(protg_WT_cols,protg_spo13_cols)]),nc=20,iter.max=50) #6?

spo13_WT_protein_clust_heatmap<-get_clust_heatmap(protg_3reps_spo13_WT_sig,protg_3reps_spo13_WT_sig.hclust,c(protg_WT_cols,protg_spo13_cols),6,"WT","spo13","spo13 v WT sigdiff proteins")
# 6 x 8 portrait

# spo13m2 v WT protein clustering
#hclust
protg_3reps_spo13m2_WT_sig.hclust<-hclust(dist(t(apply(as.matrix(protg_3reps_spo13m2_WT_sig[,c(protg_WT_cols,protg_spo13m2_cols)]),1,scale))),method="ward.D2")

# how many clusters are appropriate
wssplot(as.matrix(protg_3reps_spo13m2_WT_sig[,c(protg_WT_cols,protg_spo13m2_cols)]),nc=20,iter.max=50) #5?

spo13m2_WT_protein_clust_heatmap<-get_clust_heatmap(protg_3reps_spo13m2_WT_sig,protg_3reps_spo13m2_WT_sig.hclust,c(protg_WT_cols,protg_spo13m2_cols),6,"WT","spo13m2","spo13m2 v WT sigdiff proteins")

# spo13 v spo13m2 protein clustering
#hclust
protg_3reps_spo13_spo13m2_sig.hclust<-hclust(dist(t(apply(as.matrix(protg_3reps_spo13_spo13m2_sig[,c(protg_spo13_cols,protg_spo13m2_cols)]),1,scale))),method="ward.D2")

# how many clusters are appropriate
wssplot(as.matrix(protg_3reps_spo13_spo13m2_sig[,c(protg_spo13_cols,protg_spo13m2_cols)]),nc=20,iter.max=50) #4?

spo13_spo13m2_protein_clust_heatmap<-get_clust_heatmap(protg_3reps_spo13_spo13m2_sig,protg_3reps_spo13_spo13m2_sig.hclust,c(protg_spo13_cols,protg_spo13m2_cols),4,"spo13","spo13m2","spo13 v spo13m2 sigdiff proteins")


# add cluster col

protg_3reps_spo13_WT_sig<-protg_3reps_spo13_WT_sig %>%
    mutate(ward.cluster=cutree(spo13_WT_protein_clust_heatmap$tree_row,k=6))

protg_3reps_spo13m2_WT_sig<-protg_3reps_spo13m2_WT_sig %>%
    mutate(ward.cluster=cutree(spo13m2_WT_protein_clust_heatmap$tree_row,k=6))

# export protg clust ids
protg_3reps_spo13_WT_sig %>%
    select(Gene.name,ward.cluster) %>%
    group_by(ward.cluster) %>%
    mutate(id=row_number()) %>%
    pivot_wider(names_from=ward.cluster,values_from=Gene.name,id_cols=id) %>%
    select(-id) %>%
    rename_with(~paste0("cluster_",.x,recycle0=T)) %>%
    write.xlsx(.,"Metaphase_protg_spo13_WT_clust_ids.xlsx")

protg_3reps_spo13m2_WT_sig %>%
    select(Gene.name,ward.cluster) %>%
    group_by(ward.cluster) %>%
    mutate(id=row_number()) %>%
    pivot_wider(names_from=ward.cluster,values_from=Gene.name,id_cols=id) %>%
    select(-id) %>%
    rename_with(~paste0("cluster_",.x,recycle0=T)) %>%
    write.xlsx(.,"Metaphase_protg_spo13m2_WT_clust_ids.xlsx")

```

# Clustering of phospho-sites most different
```{r,echo=F,message=F,warning=F}

# there are far too many sites to label on the heatmap
# phosphos_3reps_WT_spo13_sig %>% nrow() #893

get_clust_heatmap_sites<-function(df,hclustdf,cols,clusternum,strain1,strain2,title){
    #cols<-gsub("nona_norm_","",cols)
    hclustdf.cutree<-cutree(hclustdf,k=clusternum)
  hclustdf.row_annots<-data.frame(cluster = as.factor(hclustdf.cutree))

  rownames(hclustdf.row_annots)<-df$gene.name_site
 rownames(df)<-df$gene.name_site
 colnames(df[,cols])<-gsub("nona_stoic_","",colnames(df[,cols]))
 
  clust.heatmap<-pheatmap(df[,cols], main=paste0(title," n=",nrow(df)),scale = 'row', clustering_method = "ward.D2",annotation_row=hclustdf.row_annots,cutree_rows = clusternum, show_rownames = F, show_colnames = T, cluster_cols = T,border_color = "NA",labels_col=gsub("nona_stoic_","",colnames(df[,cols]))
                          )
  return(clust.heatmap)
}

# clustering heatmaps

phos_WT_cols<-grep("WT",nona_phos.stoic.cols,value=T)
phos_spo13_cols<-grep("spo13_",nona_phos.stoic.cols,value=T)
phos_spo13m2_cols<-grep("spo13m2",nona_phos.stoic.cols,value=T)


# spo13 v WT sites
#hclust
phosphos_3reps_spo13_WT_sig.hclust<-hclust(dist(t(apply(as.matrix(phosphos_3reps_spo13_WT_sig[,c(phos_WT_cols,phos_spo13_cols)]),1,scale))),method="ward.D2")

# how many clusters are appropriate
wssplot(as.matrix(phosphos_3reps_spo13_WT_sig[,c(phos_WT_cols,phos_spo13_cols)]),nc=20,iter.max=50) #10

spo13_WT_phos_clust_heatmap<-get_clust_heatmap_sites(phosphos_3reps_spo13_WT_sig,phosphos_3reps_spo13_WT_sig.hclust,c(phos_WT_cols,phos_spo13_cols),10,"WT","spo13","spo13 v WT sigdiff sites")

# spo13m2 v WT sites
#hclust
phosphos_3reps_spo13m2_WT_sig.hclust<-hclust(dist(t(apply(as.matrix(phosphos_3reps_spo13m2_WT_sig[,c(phos_WT_cols,phos_spo13m2_cols)]),1,scale))),method="ward.D2")

# how many clusters are appropriate
wssplot(as.matrix(phosphos_3reps_spo13m2_WT_sig[,c(phos_WT_cols,phos_spo13m2_cols)]),nc=20,iter.max=50) #5

spo13m2_WT_phos_clust_heatmap<-get_clust_heatmap_sites(phosphos_3reps_spo13m2_WT_sig,phosphos_3reps_spo13m2_WT_sig.hclust,c(phos_WT_cols,phos_spo13m2_cols),5,"WT","spo13m2","spo13m2 v WT sigdiff sites")

# spo13 v spo13m2 sites
#hclust
phosphos_3reps_spo13_spo13m2_sig.hclust<-hclust(dist(t(apply(as.matrix(phosphos_3reps_spo13_spo13m2_sig[,c(phos_spo13_cols,phos_spo13m2_cols)]),1,scale))),method="ward.D2")

# how many clusters are appropriate
wssplot(as.matrix(phosphos_3reps_spo13_spo13m2_sig[,c(phos_spo13_cols,phos_spo13m2_cols)]),nc=20,iter.max=50) #3

spo13_spo13m2_phos_clust_heatmap<-get_clust_heatmap_sites(phosphos_3reps_spo13_spo13m2_sig,phosphos_3reps_spo13_spo13m2_sig.hclust,c(phos_spo13_cols,phos_spo13m2_cols),4,"spo13","spo13m2","spo13 v spo13m2 sigdiff sites")

# spo13_WT_phos_clust_heatmap
# spo13m2_WT_phos_clust_heatmap
# spo13_spo13m2_phos_clust_heatmap


# add cluster cols
phosphos_3reps_spo13_WT_sig<-phosphos_3reps_spo13_WT_sig %>%
    mutate(ward.cluster=cutree(spo13_WT_phos_clust_heatmap$tree_row,k=10))

phosphos_3reps_spo13m2_WT_sig<-phosphos_3reps_spo13m2_WT_sig %>%
    mutate(ward.cluster=cutree(spo13m2_WT_phos_clust_heatmap$tree_row,k=5))

phosphos_3reps_spo13_spo13m2_sig<-phosphos_3reps_spo13_spo13m2_sig %>%
    mutate(ward.cluster=cutree(spo13_spo13m2_phos_clust_heatmap$tree_row,k=4))

# export cluster lists to excel

phosphos_3reps_spo13_WT_sig %>%
    arrange(ward.cluster) %>%
    group_by(ward.cluster) %>%
    mutate(id=row_number()) %>%
    pivot_wider(names_from=ward.cluster,values_from=gene.name_site,id_cols=id) %>%
    select(-id) %>%
    rename_with(~paste0("cluster_",.x,recycle0=T)) %>%
    write.xlsx(.,file="MetaphaseI_spo13_WT_sig_phos_clust_ids.xlsx")

phosphos_3reps_spo13m2_WT_sig %>%
    arrange(ward.cluster) %>%
    group_by(ward.cluster) %>%
    mutate(id=row_number()) %>%
    pivot_wider(names_from=ward.cluster,values_from=gene.name_site,id_cols=id) %>%
    select(-id) %>%
    rename_with(~paste0("cluster_",.x,recycle0=T)) %>%
    write.xlsx(.,file="MetaphaseI_spo13m2_WT_sig_phos_clust_ids.xlsx")

phosphos_3reps_spo13_spo13m2_sig %>%
    arrange(ward.cluster) %>%
    group_by(ward.cluster) %>%
    mutate(id=row_number()) %>%
    pivot_wider(names_from=ward.cluster,values_from=gene.name_site,id_cols=id) %>%
    select(-id) %>%
    rename_with(~paste0("cluster_",.x,recycle0=T)) %>%
    write.xlsx(.,file="MetaphaseI_spo13_spo13m2_sig_phos_clust_ids.xlsx")


# MODIFIED for not clustering cols and labelling rows

# get_clust_heatmap_sites_2<-function(df,hclustdf,cols,clusternum,strain1,strain2,title){
#     #cols<-gsub("nona_norm_","",cols)
#     hclustdf.cutree<-cutree(hclustdf,k=clusternum)
#   hclustdf.row_annots<-data.frame(cluster = as.factor(hclustdf.cutree))
# 
#   rownames(hclustdf.row_annots)<-df$gene.name_site
#  rownames(df)<-df$gene.name_site
#  colnames(df[,cols])<-gsub("nona_stoic_","",colnames(df[,cols]))
#  
#   clust.heatmap<-pheatmap(df[,cols], main=paste0(title," n=",nrow(df)),scale = 'row', clustering_method = "ward.D2",annotation_row=hclustdf.row_annots,cutree_rows = clusternum, show_rownames = T, show_colnames = T, cluster_cols = F,border_color = "NA",labels_col=gsub("nona_stoic_","",colnames(df[,cols]))
#                           )
#   return(clust.heatmap)
# }
 
# DEN.STF sites clustering among all 3 comparisons
# sub DEN.STF site df

# DEN.STF_phos_df<-phosphos_3reps_loc %>% filter(grepl(".............[DEN].[ST]F..............",Sequence.window))
# 
# #hclust
# phos_DEN.STF.hclust<-hclust(dist(t(apply(as.matrix(DEN.STF_phos_df[,c(phos_WT_cols,phos_spo13_cols,phos_spo13m2_cols)]),1,scale))),method="ward.D2")
# 
# # how many clusters are appropriate
# wssplot(as.matrix(DEN.STF_phos_df[,c(phos_WT_cols,phos_spo13_cols,phos_spo13m2_cols)]),nc=20,iter.max=50) #4
# 
# DEN.STF_sites_clust<-get_clust_heatmap_sites_2(DEN.STF_phos_df,phos_DEN.STF.hclust,c(phos_WT_cols,phos_spo13_cols,phos_spo13m2_cols),4,"WT","spo13m2","All Exp40E DEN.STF sites")
# 
# print_plot(DEN.STF_sites_clust,
#            "Exp40E_DEN.STF_phos_clust_heatmap.pdf",8,14)


## DEN.STF sites
## modified to show WT_spo13 sig catgories #####
get_clust_heatmap_sites_3<-function(df,hclustdf,cols,clusternum,strain1,strain2,title){
    #cols<-gsub("nona_norm_","",cols)
    hclustdf.cutree<-cutree(hclustdf,k=clusternum)
  hclustdf.row_annots<-data.frame(WT_spo13_sig=as.factor(df$spo13_WT_sig),
                                  WT_spo13m2_sig=as.factor(df$spo13m2_WT_sig),
                                  spo13_spo13m2_sig=as.factor(df$spo13_spo13m2_sig),
                                  cluster = as.factor(hclustdf.cutree))

  rownames(hclustdf.row_annots)<-df$gene.name_site
 rownames(df)<-df$gene.name_site
 colnames(df[,cols])<-gsub("nona_stoic_","",colnames(df[,cols]))
 
  clust.heatmap<-pheatmap(df[,cols], main=paste0(title," n=",nrow(df)),scale = 'row', clustering_method = "ward.D2",annotation_row=hclustdf.row_annots,cutree_rows = clusternum, show_rownames = T, show_colnames = T, cluster_cols = F,border_color = "NA",labels_col=gsub("nona_stoic_","",colnames(df[,cols]))
                          )
  return(clust.heatmap)
}

# re plot with sig levels labeled
DEN.STF_sites_clust_3<-get_clust_heatmap_sites_3(DEN.STF_phos_df,phos_DEN.STF.hclust,c(phos_WT_cols,phos_spo13_cols,phos_spo13m2_cols),4,"WT","spo13m2","All Exp40E DEN.STF sites")

print_plot(DEN.STF_sites_clust_3,
           "Exp40E_DEN.STF_phos_clust_heatmap_siglabel.pdf",9,14)

# add cluster col to df
DEN.STF_phos_df <- DEN.STF_phos_df %>%
  mutate(ward.cluster=cutree(DEN.STF_sites_clust_3$tree_row, k= 4))


# SIG SSITES

DEN.STF_sig_phos_df<-phosphos_3reps_loc %>% filter(grepl(".............[DEN].[ST]F..............",Sequence.window)) %>%
    filter(spo13_WT_sig!="NC"|spo13m2_WT_sig!="NC")

#nrow(DEN.STF_sig_phos_df) #22

#hclust
phos_DEN.STF.sig.hclust<-hclust(dist(t(apply(as.matrix(DEN.STF_sig_phos_df[,c(phos_WT_cols,phos_spo13_cols,phos_spo13m2_cols)]),1,scale))),method="ward.D2")

# how many clusters are appropriate
wssplot(as.matrix(DEN.STF_sig_phos_df[,c(phos_WT_cols,phos_spo13_cols,phos_spo13m2_cols)]),nc=19,iter.max=50) #2

DEN.STF_sig_sites_clust<-get_clust_heatmap_sites_2(DEN.STF_sig_phos_df,phos_DEN.STF.sig.hclust,c(phos_WT_cols,phos_spo13_cols,phos_spo13m2_cols),2,"WT","spo13","WT_spo13 or WT_spo13m2 DECR Exp40E DEN.STF sites")

print_plot(DEN.STF_sig_sites_clust,
           "Exp40E_DEN.STF_sig_phos_clust_heatmap.pdf",8,6)

# addcluster col
DEN.STF_sig_phos_df <- DEN.STF_sig_phos_df %>%
  mutate(ward.cluster=cutree(DEN.STF_sig_sites_clust$tree_row, k= 2))

# export

DEN.STF_sig_clust_list<-list()

DEN.STF_sig_clust_list[[1]]<-DEN.STF_sig_phos_df %>%
    select(Gene.name,gene.name_site,ward.cluster,spo13_WT_sig,spo13m2_WT_sig)

DEN.STF_sig_clust_list[[2]]<-gost(DEN.STF_sig_phos_df %>%
         select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection)

names(DEN.STF_sig_clust_list)<-c("all_sites","all_GO_terms")

write.xlsx(DEN.STF_sig_clust_list,"DEN.STF_sig_cluster_GO.xlsx")

# any ssites sig DECR in spo13 mut v WT
# gost(DEN.STF_sig_phos_df %>%
#          select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
#     select(term_name,term_id,source,p_value,intersection) %>%
#     write_clip()

# ssites in cluter 3 or 3+2 in DEN.STF cluteirng

DEN.STF_clust_list<-list()

DEN.STF_clust_list[[1]]<-DEN.STF_phos_df %>%
    select(Gene.name,gene.name_site,ward.cluster,spo13_WT_sig,spo13m2_WT_sig)

DEN.STF_clust_list[[2]]<-gost(DEN.STF_phos_df %>%
         select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection) 

DEN.STF_clust_list[[3]]<-DEN.STF_phos_df %>%
    filter(ward.cluster==3) %>%
    select(Gene.name,gene.name_site,ward.cluster,spo13_WT_sig,spo13m2_WT_sig)

DEN.STF_clust_list[[4]]<-DEN.STF_phos_df %>%
    filter(ward.cluster==3|ward.cluster==2) %>%
    select(Gene.name,gene.name_site,ward.cluster,spo13_WT_sig,spo13m2_WT_sig)

DEN.STF_clust_list[[5]]<-gost(DEN.STF_phos_df %>%
    filter(ward.cluster==3) %>%
         select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection) 

DEN.STF_clust_list[[6]]<-gost(DEN.STF_phos_df %>%
    filter(ward.cluster==3|ward.cluster==2) %>%
         select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection) 

names(DEN.STF_clust_list)<-c("all_sites","all_sites_GO_terms","cluster_3","cluster_2_or_3","cluster_3_GO_terms","cluster_2_or_3_GO_terms")

write.xlsx(DEN.STF_clust_list,"DEN.STF_cluster_GO.xlsx")


# no row label
# get_clust_heatmap_sites_2_nolabel<-function(df,hclustdf,cols,clusternum,strain1,strain2,title){
#     #cols<-gsub("nona_norm_","",cols)
#     hclustdf.cutree<-cutree(hclustdf,k=clusternum)
#   hclustdf.row_annots<-data.frame(cluster = as.factor(hclustdf.cutree))
# 
#   rownames(hclustdf.row_annots)<-df$gene.name_site
#  rownames(df)<-df$gene.name_site
#  colnames(df[,cols])<-gsub("nona_stoic_","",colnames(df[,cols]))
#  
#   clust.heatmap<-pheatmap(df[,cols], main=paste0(title," n=",nrow(df)),scale = 'row', clustering_method = "ward.D2",annotation_row=hclustdf.row_annots,cutree_rows = clusternum, show_rownames = F, show_colnames = T, cluster_cols = F,border_color = "NA",labels_col=gsub("nona_stoic_","",colnames(df[,cols]))
#                           )
#   return(clust.heatmap)
# }

```

# Print pdfs of clustering
```{r,echo=F,message=F,warning=F}

# print to R clusterings
# WT_spo13_protein_clust_heatmap
# WT_spo13m2_protein_clust_heatmap
# spo13_spo13m2_protein_clust_heatmap
# 
# WT_spo13_phos_clust_heatmap
# WT_spo13m2_phos_clust_heatmap
# spo13_spo13m2_phos_clust_heatmap

# print to pdf clusterings
# protein 3 comparisons
print_plot(spo13_WT_protein_clust_heatmap,
           "spo13_WT_protein_clust_heatmap.pdf",6,18)


print_plot(spo13m2_WT_protein_clust_heatmap,
           "spo13m2_WT_protein_clust_heatmap.pdf",6,8)


print_plot(spo13_spo13m2_protein_clust_heatmap,
           "spo13_spo13m2_protein_clust_heatmap.pdf",6,8)

# phos 3 comparisons
print_plot(spo13_WT_phos_clust_heatmap,
           "spo13_WT_phos_clust_heatmap.pdf",5,6) 
print_plot(spo13m2_WT_phos_clust_heatmap,
           "spo13m2_WT_phos_clust_heatmap.pdf",5,6)
print_plot(spo13_spo13m2_phos_clust_heatmap,
           "spo13_spo13m2_phos_clust_heatmap.pdf",5,6)

```


# phos sig cat GO terms
```{r}

    
# GO terms enriched among spo13 v WT sigdiff sites

spo13_WT_sig_cat_GO_dfs<-list()
spo13_WT_sig_cat_GO_dfs[[1]]<-gost(phosphos_3reps_spo13_WT_sig %>%
    filter(spo13_WT_sig!="NC") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection)
spo13_WT_sig_cat_GO_dfs[[2]]<-gost(phosphos_3reps_spo13_WT_sig %>%
    filter(spo13_WT_sig=="DECR") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection)
spo13_WT_sig_cat_GO_dfs[[3]]<-gost(phosphos_3reps_spo13_WT_sig %>%
    filter(spo13_WT_sig=="INCR") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection)

names(spo13_WT_sig_cat_GO_dfs)<-c("spo13_WT_allsig","spo13_WT_DECR","spo13_WT_INCR")

write.xlsx(spo13_WT_sig_cat_GO_dfs,"spo13_WT_sig_cat_GO_terms.xlsx")

# GO terms enriched among spo13m2 v WT sigdiff sites

spo13m2_WT_sig_cat_GO_dfs<-list()
spo13m2_WT_sig_cat_GO_dfs[[1]]<-gost(phosphos_3reps_spo13m2_WT_sig %>%
    filter(spo13m2_WT_sig!="NC") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection)
spo13m2_WT_sig_cat_GO_dfs[[2]]<-gost(phosphos_3reps_spo13m2_WT_sig %>%
    filter(spo13m2_WT_sig=="DECR") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection)
spo13m2_WT_sig_cat_GO_dfs[[3]]<-gost(phosphos_3reps_spo13m2_WT_sig %>%
    filter(spo13m2_WT_sig=="INCR") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection)

names(spo13m2_WT_sig_cat_GO_dfs)<-c("spo13m2_WT_allsig","spo13m2_WT_DECR","spo13m2_WT_INCR")

write.xlsx(spo13m2_WT_sig_cat_GO_dfs,"spo13m2_WT_sig_cat_GO_terms.xlsx")


# GO terms enriched among spo13 v spo13m2 sigdiff sites

spo13_spo13m2_sig_cat_GO_dfs<-list()
spo13_spo13m2_sig_cat_GO_dfs[[1]]<-gost(phosphos_3reps_spo13_spo13m2_sig %>%
    filter(spo13_spo13m2_sig!="NC") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection)
spo13_spo13m2_sig_cat_GO_dfs[[2]]<-gost(phosphos_3reps_spo13_spo13m2_sig %>%
    filter(spo13_spo13m2_sig=="DECR") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection)
spo13_spo13m2_sig_cat_GO_dfs[[3]]<-gost(phosphos_3reps_spo13_spo13m2_sig %>%
    filter(spo13_spo13m2_sig=="INCR") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    select(term_name,term_id,source,p_value,intersection)

names(spo13_spo13m2_sig_cat_GO_dfs)<-c("spo13_spo13m2_allsig","spo13_spo13m2_DECR","spo13_spo13m2_INCR")

write.xlsx(spo13_spo13m2_sig_cat_GO_dfs,"spo13_spo13m2_sig_cat_GO_terms.xlsx")


# which GO terms are shared v unique in DECR spo13 v WT and sspo13m2 v WT

# intersect(spo13_WT_sig_cat_GO_dfs[[2]]$term_name ,spo13m2_WT_sig_cat_GO_dfs[[2]]$term_name) #137 overlap
# 
# spo13_WT_sig_cat_GO_dfs[[2]]$term_name[!spo13_WT_sig_cat_GO_dfs[[2]]$term_name %in% intersect(spo13_WT_sig_cat_GO_dfs[[2]]$term_name ,spo13m2_WT_sig_cat_GO_dfs[[2]]$term_name)] #206 unique to spo13_WT
# 
# length(spo13_WT_sig_cat_GO_dfs[[2]]$term_name) #343 terms enriched spo13_WT
# 
# #206+137 = 343
# 
# spo13m2_WT_sig_cat_GO_dfs[[2]]$term_name[!spo13m2_WT_sig_cat_GO_dfs[[2]]$term_name %in% intersect(spo13_WT_sig_cat_GO_dfs[[2]]$term_name ,spo13m2_WT_sig_cat_GO_dfs[[2]]$term_name)] #16 unique to spo13m2_WT
# 
# length(spo13m2_WT_sig_cat_GO_dfs[[2]]$term_name) #153 terms enriched spo13m2_WT
# 
# #153-137 = 16 

# export df that includes unique and intersecting GO terms from DECR spo13 v WT and spo13m2 v WT

overlap_DECR_spo13_spo13m2_phos_GO_dfs<-list()

overlap_DECR_spo13_spo13m2_phos_GO_dfs[[1]]<-spo13_WT_sig_cat_GO_dfs[[2]] %>%
    filter(term_name %in% intersect(spo13_WT_sig_cat_GO_dfs[[2]]$term_name ,spo13m2_WT_sig_cat_GO_dfs[[2]]$term_name)) # 137 GO terms overlap

overlap_DECR_spo13_spo13m2_phos_GO_dfs[[2]]<-spo13_WT_sig_cat_GO_dfs[[2]] %>%
    filter(term_name %in% spo13_WT_sig_cat_GO_dfs[[2]]$term_name[!spo13_WT_sig_cat_GO_dfs[[2]]$term_name %in% intersect(spo13_WT_sig_cat_GO_dfs[[2]]$term_name ,spo13m2_WT_sig_cat_GO_dfs[[2]]$term_name)]) # 206 GO terms unique to spo13 v WT

overlap_DECR_spo13_spo13m2_phos_GO_dfs[[3]]<-spo13m2_WT_sig_cat_GO_dfs[[2]] %>%
    filter(term_name %in% spo13m2_WT_sig_cat_GO_dfs[[2]]$term_name[!spo13m2_WT_sig_cat_GO_dfs[[2]]$term_name %in% intersect(spo13_WT_sig_cat_GO_dfs[[2]]$term_name ,spo13m2_WT_sig_cat_GO_dfs[[2]]$term_name)]) # 16 GO terms unique to spo13m2 v WT

names(overlap_DECR_spo13_spo13m2_phos_GO_dfs)<-c("spo13_spo13m2_DECR_both","spo13_DECR_unique","spo13m2_DECR_unique")

write.xlsx(overlap_DECR_spo13_spo13m2_phos_GO_dfs,"overlap_spo13_spo13m2_DECR_v_WT_phos_GO_terms.xlsx")

# export df that includes unique and intersecting GO terms from INCR spo13 v WT and spo13m2 v WT

overlap_INCR_spo13_spo13m2_phos_GO_dfs<-list()

overlap_INCR_spo13_spo13m2_phos_GO_dfs[[1]]<-spo13_WT_sig_cat_GO_dfs[[3]] %>%
    filter(term_name %in% intersect(spo13_WT_sig_cat_GO_dfs[[3]]$term_name ,spo13m2_WT_sig_cat_GO_dfs[[3]]$term_name)) # 137 GO terms overlap

overlap_INCR_spo13_spo13m2_phos_GO_dfs[[2]]<-spo13_WT_sig_cat_GO_dfs[[3]] %>%
    filter(term_name %in% spo13_WT_sig_cat_GO_dfs[[3]]$term_name[!spo13_WT_sig_cat_GO_dfs[[3]]$term_name %in% intersect(spo13_WT_sig_cat_GO_dfs[[3]]$term_name ,spo13m2_WT_sig_cat_GO_dfs[[3]]$term_name)]) # 206 GO terms unique to spo13 v WT

overlap_INCR_spo13_spo13m2_phos_GO_dfs[[3]]<-spo13m2_WT_sig_cat_GO_dfs[[3]] %>%
    filter(term_name %in% spo13m2_WT_sig_cat_GO_dfs[[3]]$term_name[!spo13m2_WT_sig_cat_GO_dfs[[3]]$term_name %in% intersect(spo13_WT_sig_cat_GO_dfs[[3]]$term_name ,spo13m2_WT_sig_cat_GO_dfs[[3]]$term_name)]) # 16 GO terms unique to spo13m2 v WT

names(overlap_INCR_spo13_spo13m2_phos_GO_dfs)<-c("spo13_spo13m2_INCR_both","spo13_INCR_unique","spo13m2_INCR_unique")

write.xlsx(overlap_INCR_spo13_spo13m2_phos_GO_dfs,"overlap_spo13_spo13m2_INCR_v_WT_phos_GO_terms.xlsx")

# select GO terms from each group and barplot:
# spo13_WT DECR 
# regulation of meiotic cell cycle GO:0051445
# histone acetylation GO:0016573
# autophagy GO:0006914
# regulation of cytoskeleton organization GO:0051493
# cortical actin cytoskeleton organization GO:0030866
# spo13_WT INCR 
# "cytoskeleton organization" GO:0007010 
# "chromatin remodeling" GO:0006338 
# cortical actin cytoskeleton organization GO:0030866
# "RNA biosynthetic process" GO:0032774 
# "prospore membrane" GO:0005628
# spo13m2_WT DECR
#  structural constituent of nuclear pore GO:0017056
#  telomere tethering at nuclear periphery GO:0034398
# spo13m2_WT INCR 
# "regulation of cell wall organization or biogenesis" GO:1903338

#meiotic cell cycle GO:0051321

# double sided barplots
# 4 colors
# spo13 INCR
# spo13 DECR
# spo13m2 INCR
# spo13m2 DECR


all_terms<-c("GO:0007010","GO:0006338", "GO:0030866","GO:0032774","GO:0005628","GO:0051321","GO:0016573","GO:0006914","GO:0051493","GO:0030866","GO:1903338","GO:0017056","GO:0034398","GO:0098813","GO:0007051")

# spo13 and spo13m2 DECR phospho-proteins enriched terms
phos_prot_GO_bar<-rbind(spo13_INCR=gost(phosphos_3reps_spo13_WT_sig %>%
    filter(spo13_WT_sig=="INCR") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    filter(term_id %in% all_terms) %>%
    select(term_name,term_id,p_value),
spo13_DECR=gost(phosphos_3reps_spo13_WT_sig %>%
    filter(spo13_WT_sig=="DECR") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    filter(term_id %in% all_terms) %>%
    select(term_name,term_id,p_value),
spo13m2_INCR=gost(phosphos_3reps_spo13m2_WT_sig %>%
    filter(spo13m2_WT_sig=="INCR") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    filter(term_id %in% all_terms) %>%
    select(term_name,term_id,p_value),
spo13m2_DECR=gost(phosphos_3reps_spo13m2_WT_sig %>%
    filter(spo13m2_WT_sig=="DECR") %>% select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
    filter(term_id %in% all_terms) %>%
    select(term_name,term_id,p_value)) %>%
    mutate(direction=ifelse(grepl("INCR",rownames(.)),"INCR","DECR")) %>%
    mutate(p_value=ifelse(grepl("DECR",direction),log10(p_value),-log10(p_value))) %>%
    mutate(sample=gsub("(.+)_(.+)","\\1",rownames(.))) %>%
    ggplot(aes(x=term_name,y=p_value,fill=interaction(direction,sample)))+
    geom_bar(stat="identity",position="identity")+
    theme_classic()+
    theme(axis.text.x=element_text(angle=90),axis.text=element_text(size=rel(1)))+
    labs(x="",y="log10(p-value)",title="metaphase I sig changed phospho-proteins")+
    coord_flip()+
    scale_y_continuous(labels=label_number(accuracy=1))

print_plot(phos_prot_GO_bar,"spo13_spo13m2_phos_prot_GO_bar.pdf",13,4)


```

# DEN.STF GO bar
```{r}

# how many unique phospho-proteins have the motif
# phosphos_3reps_loc %>%
#     filter(grepl(".............[DEN].[ST]F..............",Sequence.window)) %>%
#     distinct(Gene.name) %>% nrow() #74

# chromosome organization GO:0051276
# meiotic chromosome separation GO:0051307
# chromatin binding GO:0003682
# nuclear division GO:0000280
# sexual reproduction GO:0019953

DEN.STF_terms<-c("GO:0051276","GO:0051307","GO:0003682","GO:0000280","GO:0019953")


DEN.STF_meta_GO_bar<-gost(phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]F..............",Sequence.window)) %>%
        select(Gene.name) %>% unlist(),organism='scerevisiae',evcodes=T, significant=T)$result %>%
   filter(term_id %in% DEN.STF_terms) %>%
    select(term_name,term_id,p_value) %>%
    # mutate(direction=ifelse(grepl("INCR",rownames(.)),"INCR","DECR")) %>%
    # mutate(p_value=ifelse(grepl("DECR",direction),log10(p_value),-log10(p_value))) %>%
    #mutate(sample=gsub("(.+)_(.+)","\\1",rownames(.))) %>%
    ggplot(aes(x=term_name,y=-log10(p_value),fill=term_name))+
    geom_bar(stat="identity",position="identity")+
    theme_classic()+
    theme(axis.text.x=element_text(angle=90),axis.text=element_text(size=rel(1)),legend.position="none")+
    labs(x="",y="-log10(p-value)",title="metaphase I [DEN].[ST]*F phospho-proteins")+
    coord_flip()+
    scale_y_continuous(labels=label_number(accuracy=1),expand=expansion(mult=c(0,0.1)))


print_plot(DEN.STF_meta_GO_bar,
           "DEN.STF_meta_GO_bar.pdf",10,3)

```



# Selected proteins lineplots #D
```{r,echo=F,message=F,warning=F}

# cell_cycle_proteins<-c("SGO1","NDT80","NDC80","CLB1","CLB4","CLB3","CLB2","CLB5","CLB6","PDS1","SPO13","CDC20","AMA1","MND2","APC2","RIM4","REC8","MAM1","ZIP1")
# 
# # mutate(fc_trimmed=ifelse(fold_change>2.2,2.2,
# #                              ifelse(fold_change<0.2,0.2,fold_change))) %>%
# 
# cell_cycle_proteins_plot<-protg_3reps %>%
#     filter(Gene.name %in% cell_cycle_proteins) %>%
#     select(Gene.name,all_of(fcs)) %>%
#     pivot_longer(-Gene.name,values_to="fold_change",names_to="sample") %>%
#     ggplot(aes(x=sample,y=Gene.name,fill=log2(fold_change))) +
#     geom_tile()+
#     scale_fill_stepsn(colors=c('#b2182b','#ef8a62','#fddbc7',
#                              '#f7f7f7','#d1e5f0','#67a9cf','#2166ac'),oob=squish_infinite,na.value="#cccccc",
#              n.breaks=10, show.limits=T)+
#  theme(axis.text.x = element_text(angle=90,vjust=0.6))+
#     labs(title="cell cycle regulated proteins",x="",y="")
# 
# kinetochore<-c("NDC10","CEP3","CTF13","SKP1","MIF2","CSE4","CTF19","OKP1","MCM21","AME1","CHL4","CNN1","WIP1","MHF1","MHF2","MCM16","CTF3","MCM22","IML3","NKP1","NKP2","YBP2","CBF1","IPL1","SLI15","NBL1","BIR1","MTW1","DSN1","NNF1","NSL1","NDC80","NUF2","SPC24","SPC25","SPC105","KRE28","ASK1","DAD1","DAD2","DAD3","DAD4","DAM1","DUO1","SPC19","SPC34","HSK1","MAD1","MAD2","BUB1","BUB3","MPS1","KIP1","KIP3","CIN8","KAR3","SLK19","BIK1","STU1","STU2")
# 
# # 
# # because the range of scale is so large, can't see differences between strains
# # protg_3reps %>%
# #     filter(Gene.name %in% kinetochore) %>%
# #     select(Gene.name,all_of(nona_norm.tmt.cols)) %>%
# #     #mutate(across(all_of(nona_norm.tmt.cols),function(x) x/mean(x))) %>%
# #     pivot_longer(-Gene.name,values_to="intensity",names_to="sample",names_prefix="nona_norm_") %>%
# #     ggplot(aes(x=sample,y=Gene.name,fill=log2(intensity))) +
# #     geom_tile()+
# #     scale_fill_viridis_c()+
# #  theme(axis.text.x = element_text(angle=90,vjust=0.6))
# 
# 
# kinetochore_proteins_plot<-protg_3reps %>%
#     filter(Gene.name %in% kinetochore) %>%
#     select(Gene.name,all_of(fcs)) %>%
#     pivot_longer(-Gene.name,values_to="fold_change",names_to="sample") %>%
#     ggplot(aes(x=sample,y=Gene.name,fill=log2(fold_change))) +
#     geom_tile()+
#     scale_fill_stepsn(colors=c('#b2182b','#ef8a62','#fddbc7',
#                              '#f7f7f7','#d1e5f0','#67a9cf','#2166ac'),
#              n.breaks=10, show.limits=T)+
#  theme(axis.text.x = element_text(angle=90,vjust=0.6))+
#     labs(title="kinetochore proteins",x="",y="")
# 
# # from berchowitz
# #clb3_co_clustered<-c("CLB3","GIP1","SPS1","YSP2","YFL012W","SPO20") # listed in berchowitz ssupp, colored in Rim4 IP in main figure
# 
# #ama1_co_clustered<-c("AMA1","YDR042C","CTS2","SPR6","YGL230C","SGA1","YNL155W","YOR214C","SSP2","SPS4")
# 
# #ime2_reg_genes<-c("CLB3","YSP2","SPO20","GIP1","STV1","SPS1","ECM8","YGL012W","HXT14") ## this longer list of 'clb3 co-clsutered' genes listed in main text of berchowitz in beginning of Ime2 reg section
# 
# #cdc5_co_clustered<-c("CDC5","YDL186W","CLB4","YJL043W","YML199W","YBR250W","YEH1","YJR107W","SPO12","TEP1","SPO75","HST3","TIM18","YGL138C","SGO1","YOL047C","MUM3","YKR005C","YAL018C","PES4","HST1","SPO21","YOR024W","TID3","STO1","CBC2")
# 
# rim4_bound_genes<-c("CLB3","YSP2","SPO20","GIP1","STV1","SPS1","ECM8","YFL012W","HXT14")
# 
# ama1_co_reg_clust<-c("AMA1","YDR042C","CTS2","SPR6","YGL230C","SGA1","YNL155W","YOR214C","SSP2","SPS4")
# 
# rim4_bound_genes_plot<-protg_3reps %>%
#     filter(Gene.name %in% rim4_bound_genes) %>%
#     select(Gene.name,all_of(fcs)) %>%
#     pivot_longer(-Gene.name,values_to="fold_change",names_to="sample") %>%
#     ggplot(aes(x=sample,y=Gene.name,fill=log2(fold_change))) +
#     geom_tile()+
#     scale_fill_stepsn(colors=c('#b2182b','#ef8a62','#fddbc7',
#                              '#f7f7f7','#d1e5f0','#67a9cf','#2166ac'),
#              n.breaks=10, show.limits=T)+
#  theme(axis.text.x = element_text(angle=90,vjust=0.6))+
# labs(title="Rim4-bound genes",x="",y="")
# 
# ama1_coreg_genes_plot<-protg_3reps %>%
#     filter(Gene.name %in% ama1_co_reg_clust) %>%
#     select(Gene.name,all_of(fcs)) %>%
#     pivot_longer(-Gene.name,values_to="fold_change",names_to="sample") %>%
#     ggplot(aes(x=sample,y=Gene.name,fill=log2(fold_change))) +
#     geom_tile()+
#     scale_fill_stepsn(colors=c('#b2182b','#ef8a62','#fddbc7',
#                              '#f7f7f7','#d1e5f0','#67a9cf','#2166ac'),
#              n.breaks=10, show.limits=T)+
#  theme(axis.text.x = element_text(angle=90,vjust=0.6))+
#     labs(title="Ama1 co-regulated genes (Brar 2012)",x="",y="")
# 
# monoorientation_proteins_plot<-protg_3reps %>%
#     filter(Gene.name %in% c("CDC5","HRR25","CSM1","LRS4","MAM1","CDC7","RTS1","SGO1")) %>%
#     select(Gene.name,all_of(fcs)) %>%
#     pivot_longer(-Gene.name,values_to="fold_change",names_to="sample") %>%
#     ggplot(aes(x=sample,y=Gene.name,fill=log2(fold_change))) +
#     geom_tile()+
#     scale_fill_stepsn(colors=c('#b2182b','#ef8a62','#fddbc7',
#                              '#f7f7f7','#d1e5f0','#67a9cf','#2166ac'),
#              n.breaks=10, show.limits=T)+
#  theme(axis.text.x = element_text(angle=90,vjust=0.6))+
#     labs(title="Mono-orientation proteins",x="",y="")
# 
# 
# (cell_cycle_proteins_plot+kinetochore_proteins_plot)/
#     (rim4_bound_genes_plot+ama1_coreg_genes_plot)
# 
# print_plot(cell_cycle_proteins_plot,"Exp40E_cell_cycle_proteins_heatmap.pdf",4,5)
# 
# print_plot(kinetochore_proteins_plot,"Exp40E_kinetochore_proteins_heatmap.pdf",4,7)
# 
# print_plot(rim4_bound_genes_plot,"Exp40E_rim4_bound_genes_heatmap.pdf",4,5)
# 
# print_plot(ama1_coreg_genes_plot,"Exp40E_ama1_coreg_genes_heatmap.pdf",4,5)
# 
# print_plot(monoorientation_proteins_plot,"Exp40E_monoorientation_proteins_heatmap.pdf",4,5)
# 
# 
# # scaled_nona_norm.tmt.cols<-paste0("scaled_",nona_norm.tmt.cols)
# # 
# # # add mean-scaled cols
# # protg_3reps[,scaled_nona_norm.tmt.cols]<- t(apply(protg_3reps[,nona_norm.tmt.cols],1, function(x) x/mean(x,na.rm=T)))
# # 
# # protg_scaled_WT_cols<-grep("WT",scaled_nona_norm.tmt.cols,value=T)
# # protg_scaled_spo13_cols<-grep("spo13_",scaled_nona_norm.tmt.cols,value=T)
# # protg_scaled_spo13m2_cols<-grep("spo13m2",scaled_nona_norm.tmt.cols,value=T)
# 
# # Pds1 protein
# protg_3reps %>%
#     filter(Gene.name=="PDS1") %>%
#     select(Gene.name,all_of(c(protg_scaled_WT_cols,protg_scaled_spo13_cols))) %>%
#     pivot_longer(-Gene.name,values_to="intensity",names_to="sample",names_prefix="scaled_nona_norm_") %>%
#     ggplot(aes(x=sample,y=Gene.name,fill=log10(intensity))) +
#     geom_tile()+
#     scale_fill_distiller(palette="RdBu")+
#  theme(axis.text.x = element_text(angle=90,vjust=0.6))+
#     labs(title="WT v spo13 Pds1",x="",y="")+
#     theme_minimal()+
#     coord_flip()
# 
# protg_3reps %>%
#     filter(Gene.name=="PDS1") %>%
#     select(Gene.name,all_of(c(protg_WT_cols,protg_spo13_cols,protg_spo13m2_cols))) %>%
#     pivot_longer(-Gene.name,values_to="intensity",names_to="sample",names_prefix="nona_norm_") %>%
#     ggplot(aes(x=sample,y=Gene.name,fill=log2(intensity))) +
#     geom_tile()+
#     scale_fill_distiller(palette="RdBu")+
#  theme(axis.text.x = element_text(angle=90,vjust=0.6))+
#     labs(title="Metaphase I Pds1 protein",x="",y="")+
#     theme_minimal()+
#     coord_flip()
# 
# phosphos_3reps_loc %>%
#     filter(Gene.name=="PDS1") %>%
#     select(gene.name_site,all_of(c(phos_WT_cols,phos_spo13_cols,phos_spo13m2_cols))) %>%
#     pivot_longer(-gene.name_site,values_to="intensity",names_to="sample",names_prefix="nona_stoic_") %>%
#     ggplot(aes(x=sample,y=gene.name_site,fill=log2(intensity))) +
#     geom_tile()+
#     labs(title="Metaphase I Pds1 sites",x="",y="")+
#     theme_minimal()+
#     scale_fill_distiller(palette="RdBu")+
#  theme(axis.text.x = element_text(angle=90,vjust=0.6))
# 
# 
# 
```


# Number of sites per protein
```{r,echo=F,message=F,warning=F}

# total number of sites per protein
# have to use unfiltered df for number of observations between strains otherwise they all have it

rep_cols_3<-c("WT.3reps","spo13.3reps","spo13m2.3reps")

# summary of how many sites are detected in all 3 strains
phosphos %>%
    filter(Localization.prob>0.75) %>%
    select(Gene.name,gene.name_site,WT.3reps,spo13.3reps,spo13m2.3reps) %>%
   mutate(strains = apply(.[,rep_cols_3],1,function(x) sum(x))) %>%
   ungroup() %>%
    group_by(strains) %>%
    summarize(n=n()) %>%
    ggplot(aes(x=strains,y=n))+
    geom_bar(stat="identity")+
    theme_classic()+
    theme(legend.position="none")

# summary of how many sites are detected in all 10 samples
#  ISSUE IS THERE ARE ABOUT 4000 SITES in PHOSPHOS THAT ARE ONLY DETECTED in ___2 and ___3 columns
#  how to exclude these from teh counts??
#  I just excluded 0 in any of the ___1 columns (which also gets rid of ___2 and ___3 sites)
phosphos %>%
    filter(Localization.prob>0.75) %>%
    select(Gene.name,gene.name_site,nona_phos.stoic.cols) %>%
   mutate(samples = apply(.[,nona_phos.stoic.cols],1,function(x) sum(x>0))) %>%
   ungroup() %>%
    group_by(samples) %>%
    summarize(n=n()) %>%
    filter(samples!=0) %>%
    mutate(samples=as.factor(samples))%>%
    ggplot(aes(x=fct_inorder(samples),y=n,fill=samples))+
    geom_bar(aes(fill=samples),stat="identity")+
    theme_classic()+
    theme(legend.position="none")+
    labs(x="number of TMT samples",y="number of sites")

nrow(phosphos_3reps_loc) #6927 sites have high loc score and detected in 3/3 reps of all strains (not necessarily 4th rep of WT)

# no localization score cutoff
phosphos %>%
    select(Gene.name,gene.name_site,nona_phos.stoic.cols) %>%
   mutate(samples = apply(.[,nona_phos.stoic.cols],1,function(x) sum(x>0))) %>%
   ungroup() %>%
    group_by(samples) %>%
    summarize(n=n()) %>%
    filter(samples!=0) %>%
    mutate(samples=as.factor(samples))%>%
    ggplot(aes(x=fct_inorder(samples),y=n,fill=samples))+
    geom_bar(aes(fill=samples),stat="identity")+
    theme_classic()+
    theme(legend.position="none")+
    labs(x="number of TMT samples",y="number of sites")


# number of sites per protein in each strain
# 3/3 reps detection
# if site is in 3 reps of any ssample it is counted
# site that is not in 3/3 reps of one sample can be counted and have site count 0 in a sample
# in thiss case 0 means it was not detected in 3/3 reps of that sample/sstrain but could've been in another sample/Strain
test<-phosphos %>%
    filter(Localization.prob>0.75) %>%
    select(Gene.name,gene.name_site,WT.3reps,spo13.3reps,spo13m2.3reps) %>% 
    group_by(Gene.name) %>%
    mutate(WT_sites=ifelse(WT.3reps==T,n(),0)) %>%
    ungroup() %>%
    group_by(Gene.name) %>%
    mutate(spo13_sites=ifelse(spo13.3reps==T,n(),0)) %>%
    ungroup() %>%
    group_by(Gene.name) %>%
    mutate(spo13m2_sites=ifelse(spo13m2.3reps==T,n(),0)) %>%
    ungroup() %>%
    select(Gene.name,WT_sites,spo13_sites,spo13m2_sites) %>% 
    distinct(Gene.name,.keep_all=T)

# number of sites per protein, sites found in 2/3 reps of the strain
# test2<-phosphos %>%
#     filter(Localization.prob>0.75) %>%
#     select(Gene.name,gene.name_site,WT.2reps,spo13.2reps,spo13m2.2reps) %>% 
#     group_by(Gene.name) %>%
#     mutate(WT_sites=ifelse(WT.2reps==T,n(),0)) %>%
#     ungroup() %>%
#     group_by(Gene.name) %>%
#     mutate(spo13_sites=ifelse(spo13.2reps==T,n(),0)) %>%
#     ungroup() %>%
#     group_by(Gene.name) %>%
#     mutate(spo13m2_sites=ifelse(spo13m2.2reps==T,n(),0)) %>%
#     ungroup() %>%
#     select(Gene.name,WT_sites,spo13_sites,spo13m2_sites) %>% 
#     distinct(Gene.name,.keep_all=T)

# test %>%
#    rowwise %>% 
#    mutate(same = n_distinct(unlist(across(all_of(c("WT_sites","spo13_sites","spo13m2_sites")), 
#         ~ as.character(.x)))) == 1) %>%
#    ungroup() %>%
#     filter(same==T) %>% nrow() # 2435/2530=0.96 sites are same number of sites across strains
# (2530-2435)/2530 # 0.04 proteins are not same number of sites per protein

# 2478/2530
# test2 %>%
#    rowwise %>%
#    mutate(same = n_distinct(unlist(across(all_of(c("WT_sites","spo13_sites","spo13m2_sites")),
#         ~ as.character(.x)))) == 1) %>%
#    ungroup() %>%
#     filter(same==T) %>% nrow() # 2478/2530=0.98 sites are same number of sites across strains
# (2530-2478)/2530 # 0.04 proteins are not same number of sites per protein

# histogram of sites per protein by sample
# detected in 3/3 reps
test %>%
    pivot_longer(-Gene.name,names_to="sample",values_to="sites") %>%
    ggplot(aes(y=sites,group=sample,fill=sample))+
    geom_histogram(position="dodge")+
    facet_wrap(~sample)+
    theme_classic()+
    theme(legend.position="none")
    
# boxplot of sites per protein by sample
test_pivot<-test %>%
    pivot_longer(-Gene.name,names_to="sample",values_to="sites") 
 
# boxplot of number of phospho-sites per protein in each strain   
num_sites_per_prot_box<-test_pivot %>%
    ggplot(aes(x=sample,y=sites,group=sample,fill=sample))+
    geom_boxplot(position="dodge")+
    geom_text(aes(x= sample, y = median(sites) , label =median(sites)), position=position_dodge(width = 0.8),size = 2.5, vjust = -0.5)+
    coord_cartesian(ylim = quantile(test_pivot$sites, c(0.1, 0.9)))+
    #facet_wrap(~sample)+
    theme_classic()+
    theme(legend.position="none")

print_plot(num_sites_per_prot_box,
           "num_sites_per_prot_boxplot.pdf",4,6)


# because most sites are found in 10/10 TMT channels (intensity>0),
# need to set a higher threshold to cutout low intensity?
# 
# or filter by sigdiff sites between strains
# then sumamrize to phospho-protein number of sites

# of proteins that have at least 1 sigdiff betweetn strains site, 
# what is average site number per protein
WT_spo13_sig_phos_prot<-phosphos %>%
    filter(Localization.prob>0.75) %>%
    filter(spo13_WT_sig!="NC") %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    select(Gene.name,gene.name_site,WT.3reps,spo13.3reps,spo13m2.3reps) %>%
    group_by(Gene.name) %>%
    mutate(WT_sites=ifelse(WT.3reps==T,n(),0)) %>%
    ungroup() %>%
    group_by(Gene.name) %>%
    mutate(spo13_sites=ifelse(spo13.3reps==T,n(),0)) %>%
    ungroup() %>%
    group_by(Gene.name) %>%
    mutate(spo13m2_sites=ifelse(spo13m2.3reps==T,n(),0)) %>%
    ungroup() %>%
    select(Gene.name,WT_sites,spo13_sites,spo13m2_sites) %>%
    distinct(Gene.name,.keep_all=T)

WT_spo13_sig_phos_prot_sites <- WT_spo13_sig_phos_prot %>%
    pivot_longer(-Gene.name,names_to="sample",values_to="sites")


WT_spo13_sig_phos_prot_sites %>%
    ggplot(aes(x=sample,y=sites,group=sample,fill=sample))+
    geom_boxplot(position="dodge")+
     geom_text(aes(x= sample, y = median(sites,na.rm=T) , label =median(sites)), position=position_dodge(width = 0.8),size = 2.5, vjust = -0.5)+
    #coord_cartesian(ylim = quantile(WT_spo13_sig_phos_prot_sites$sites, c(0.1, 0.9)))+
    #facet_wrap(~sample)+
    theme_classic()+
    theme(legend.position="none")
#median is 1 phospho-site per protein among proteins with at least 1 site that is sigdiff pphos between WT and spo13d
#
#histogram instead of boxplot
WT_spo13_sig_phos_prot %>%
    pivot_longer(-Gene.name,names_to="sample",values_to="sites") %>%
    ggplot(aes(y=sites,group=sample,fill=sample))+
    geom_histogram(position="dodge")+
    facet_wrap(~sample)+
    theme_classic()+
    theme(legend.position="none")

```

# Percent Polo sites sigdiff METAPHASE pie
```{r}

perc_polo_sigdiff_metaI_pie<-phosphos_3reps_loc %>%
    filter(grepl(".............[DEN].[ST]...............",Sequence.window)) %>%
    group_by(spo13_WT_sig) %>% summarize(n=n()) %>%
ggplot(aes(x="",y=n,fill=spo13_WT_sig,label=n))+
    geom_bar(stat="identity")+
    geom_label_repel()+
    coord_polar("y", start=0)+
    theme_void()+
    scale_fill_manual(values=c("#7CAE00", "#00BFC4", "#C77CFF","blue"))+
    ggtitle("Meta I sigdiff Polo sites")+
    theme(legend.title=element_blank())

print_plot(perc_polo_sigdiff_metaI_pie,
           "perc_polo_sigdiff_metaI_pie.pdf",5,5)


```


# Number of sigdiff Polo sites barplot
```{r,echo=F,message=F,warning=F}


motif_sigcat_numbers_barplot<-function(df,motif,comp,title){
    df %>%
    filter(grepl(motif,Sequence.window)) %>% 
    group_by(.data[[comp]]) %>%
    summarize(n=n()) %>%
    ggplot(aes(x=.data[[comp]],y=n,fill=.data[[comp]]))+
    geom_bar(aes(fill=.data[[comp]]),stat="identity")+
    geom_text(aes(label=n),vjust=-1)+
        scale_y_continuous(expand=expansion(mult=c(0,0.2)))+
    theme_classic()+
    theme(axis.text.x = element_text(angle=90,vjust=0.6),legend.position="none",axis.line=element_line(linewidth=0.25))+
    labs(y="number of of sites",x="",title=title)
}

WT_spo13_DEN_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,".............[DEN].[ST]...............","spo13_WT_sig","[DEN].[ST] phospho-sites WT v spo13")
WT_spo13m2_DEN_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,".............[DEN].[ST]...............","spo13m2_WT_sig","[DEN].[ST] phospho-sites WT v spo13m2")
spo13_spo13m2_DEN_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,".............[DEN].[ST]...............","spo13_spo13m2_sig","[DEN].[ST] phospho-sites spo13 v spo13m2")


WT_spo13_DEN_sigcat_barplot+WT_spo13m2_DEN_sigcat_barplot+spo13_spo13m2_DEN_sigcat_barplot

print_plot(WT_spo13_DEN_sigcat_barplot+WT_spo13m2_DEN_sigcat_barplot+spo13_spo13m2_DEN_sigcat_barplot,
           "DEN_sigcat_barplot.pdf",13,4)

```

# Number of sigdiff CDK sites barplot
```{r,echo=F,message=F,warning=F}
# Minimal CDK STP
# 
# phosphos_3reps_loc %>% 
#     filter(grepl("...............[ST]P..............",Sequence.window)) %>% nrow() #1444 min CDK sites in all 9/10 samples

WT_spo13_SP_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,"...............[ST]P..............","spo13_WT_sig","[ST]P phospho-sites WT v spo13")
WT_spo13m2_SP_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,"...............[ST]P..............","spo13m2_WT_sig","[ST]P phospho-sites WT v spo13m2")
spo13_spo13m2_SP_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,"...............[ST]P..............","spo13_spo13m2_sig","[ST]P phospho-sites spo13 v spo13m2")

print_plot(WT_spo13_SP_sigcat_barplot+WT_spo13m2_SP_sigcat_barplot+spo13_spo13m2_SP_sigcat_barplot,
           "SP_sigcat_barplot.pdf",13,4)

# strict CDK sites
# phosphos_3reps_loc %>% 
#     filter(grepl("...............[ST]P.[KR]............",Sequence.window)) %>% nrow() #246 strict CDK sites in all 9/10 samples
    
WT_spo13_SPKR_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,"...............[ST]P.[KR]............","spo13_WT_sig","[ST]P.[KR] phospho-sites WT v spo13")
WT_spo13m2_SPKR_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,"...............[ST]P.[KR]............","spo13m2_WT_sig","[ST]P.[KR] phospho-sites WT v spo13m2")

# has to be manually made to add back missing INCR col
spo13_spo13m2_SPKR_sigcat_barplot<-phosphos_3reps_loc %>%
    filter(grepl("...............[ST]P.[KR]............",Sequence.window)) %>% 
    group_by(spo13_spo13m2_sig) %>%
    summarize(n=n()) %>%
    rbind(c("INCR","0")) %>%
    mutate(spo13_spo13m2_sig=factor(spo13_spo13m2_sig,levels=c("DECR","INCR","NC"))) %>%
    mutate(n=as.numeric(n)) %>%
    ggplot(aes(spo13_spo13m2_sig,y=n,fill=spo13_spo13m2_sig))+
    geom_bar(aes(fill=spo13_spo13m2_sig),stat="identity")+
    geom_text(aes(label=n),vjust=-1)+
        scale_y_continuous(expand=expansion(mult=c(0,0.2)))+
    theme_classic()+
    theme(axis.text.x = element_text(angle=90,vjust=0.6),legend.position="none",axis.line=element_line(linewidth=0.25))+
    labs(y="number of of sites",x="",title="[ST]P.[KR] phospho-sites spo13 v spo13m2")
    

print_plot(WT_spo13_SPKR_sigcat_barplot+WT_spo13m2_SPKR_sigcat_barplot+spo13_spo13m2_SPKR_sigcat_barplot,
           "SP.KR_sigcat_barplot.pdf",13,4)

```

# Number sigdiff RK.ST sites barplot
```{r,echo=F,message=F,warning=F}

#RK.ST sites
#
WT_spo13_KR.ST_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,".............[KR].[ST]P..............","spo13_WT_sig","[RK].[ST] phospho-sites WT v spo13")
WT_spo13m2_KR.ST_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,".............[KR].[ST]P..............","spo13m2_WT_sig","[RK].[ST] phospho-sites WT v spo13m2")

# spo13 v spo13_m2 has to be manually made since there are no INCR sites and the row has to be added back
spo13_spo13m2_KR.ST_sigcat_barplot<-phosphos_3reps_loc %>%
    filter(grepl(".............[KR].[ST]P..............",Sequence.window)) %>% 
    group_by(spo13_spo13m2_sig) %>%
    summarize(n=n()) %>%
    rbind(c("INCR","0")) %>%
    mutate(spo13_spo13m2_sig=factor(spo13_spo13m2_sig,levels=c("DECR","INCR","NC"))) %>%
    mutate(n=as.numeric(n)) %>%
    ggplot(aes(spo13_spo13m2_sig,y=n,fill=spo13_spo13m2_sig))+
    geom_bar(aes(fill=spo13_spo13m2_sig),stat="identity")+
    geom_text(aes(label=n),vjust=-1)+
        scale_y_continuous(expand=expansion(mult=c(0,0.2)))+
    theme_classic()+
    theme(axis.text.x = element_text(angle=90,vjust=0.6),legend.position="none",axis.line=element_line(linewidth=0.25))+
    labs(y="number of of sites",x="",title="[RK].[ST] phospho-sites spo13 v spo13m2")


print_plot(WT_spo13_KR.ST_sigcat_barplot+WT_spo13m2_KR.ST_sigcat_barplot+spo13_spo13m2_KR.ST_sigcat_barplot,
           "KR.ST_sigcat_barplot.pdf",13,4)

#RK..ST sites

WT_spo13_KR..ST_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,"............[KR]..[ST]...............","spo13_WT_sig","[RK]..[ST] phospho-sites WT v spo13")
WT_spo13m2_KR..ST_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,"............[KR]..[ST]...............","spo13m2_WT_sig","[RK]..[ST] phospho-sites WT v spo13m2")
spo13_spo13m2_KR..ST_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,"............[KR]..[ST]...............","spo13_spo13m2_sig","[RK]..[ST] phospho-sites WT v spo13m2")

print_plot(WT_spo13_KR..ST_sigcat_barplot+WT_spo13m2_KR..ST_sigcat_barplot+spo13_spo13m2_KR..ST_sigcat_barplot,
           "KR..ST_sigcat_barplot.pdf",13,4)

# KRKR.ST sites
WT_spo13_KRKR.ST_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,"............[KR][KR].[ST]...............","spo13_WT_sig","[RK][RK].[ST] phospho-sites WT v spo13")
WT_spo13m2_KRKR.ST_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,"............[KR][KR].[ST]...............","spo13m2_WT_sig","[RK][RK].[ST] phospho-sites WT v spo13m2")
spo13_spo13m2_KRKR.ST_sigcat_barplot<-motif_sigcat_numbers_barplot(phosphos_3reps_loc,"............[KR][KR].[ST]...............","spo13_spo13m2_sig","[RK][RK].[ST] phospho-sites WT v spo13m2")

print_plot(WT_spo13_KRKR.ST_sigcat_barplot+WT_spo13m2_KRKR.ST_sigcat_barplot+spo13_spo13m2_KRKR.ST_sigcat_barplot,
           "KRKR.ST_sigcat_barplot.pdf",13,4)

```

# export sigcat ids

```{r}


# spo13 v WT protg sig cats
protg_3reps %>%
   #mutate(Sequence.window_5=substr(Sequence.window,11,21)) %>%
    select(Gene.name,spo13_WT_sig) %>%
    arrange(spo13_WT_sig) %>%
    mutate(spo13_WT_sig=factor(spo13_WT_sig,levels=c("NC","INCR","DECR"))) %>%
    arrange(spo13_WT_sig) %>%
    group_by(spo13_WT_sig) %>%
    mutate(id=row_number()) %>% 
    pivot_wider(names_from=spo13_WT_sig,values_from=Gene.name,id_cols=id) %>%
    select(-id) %>%
    write.xlsx(.,"Metaphase_protg_spo13_WT_sigcat_ids.xlsx")

protg_3reps %>%
   #mutate(Sequence.window_5=substr(Sequence.window,11,21)) %>%
    select(Gene.name,spo13m2_WT_sig) %>%
    arrange(spo13m2_WT_sig) %>%
    mutate(spo13m2_WT_sig=factor(spo13m2_WT_sig,levels=c("NC","INCR","DECR"))) %>%
    arrange(spo13m2_WT_sig) %>%
    group_by(spo13m2_WT_sig) %>%
    mutate(id=row_number()) %>% 
    pivot_wider(names_from=spo13m2_WT_sig,values_from=Gene.name,id_cols=id) %>%
    select(-id) %>%
    write.xlsx(.,"Metaphase_protg_spo13m2_WT_sigcat_ids.xlsx")


# phos sigcat ids
# single sheet with different columns for each sigdiff category

# spo13 v WT phos sig cats
phosphos_3reps_loc %>%
   #mutate(Sequence.window_5=substr(Sequence.window,11,21)) %>%
    select(gene.name_site,spo13_WT_sig) %>%
    arrange(spo13_WT_sig) %>%
    mutate(spo13_WT_sig=factor(spo13_WT_sig,levels=c("NC","INCR","DECR"))) %>%
    arrange(spo13_WT_sig) %>%
    group_by(spo13_WT_sig) %>%
    mutate(id=row_number()) %>% 
    pivot_wider(names_from=spo13_WT_sig,values_from=gene.name_site,id_cols=id) %>%
    select(-id) %>%
    write.xlsx(.,"Metaphase_phos_spo13_WT_sigcat_ids.xlsx")

# spo13m2 v WT phos sig cats
phosphos_3reps_loc %>%
   #mutate(Sequence.window_5=substr(Sequence.window,11,21)) %>%
    select(gene.name_site,spo13m2_WT_sig) %>%
    arrange(spo13m2_WT_sig) %>%
    mutate(spo13m2_WT_sig=factor(spo13m2_WT_sig,levels=c("NC","INCR","DECR"))) %>%
    arrange(spo13m2_WT_sig) %>%
    group_by(spo13m2_WT_sig) %>%
    mutate(id=row_number()) %>% 
    pivot_wider(names_from=spo13m2_WT_sig,values_from=gene.name_site,id_cols=id) %>%
    select(-id) %>%
    write.xlsx(.,"Metaphase_phos_spo13m2_WT_sigcat_ids.xlsx")


```


# export results tables for cross-analysis with timecourse
```{r,echo=F,message=F,warning=F}

write.csv(protg_3reps,"Exp40E_protg.csv")
write.csv(phosphos_3reps_loc,"Exp40E_phos.csv")

```